---
title: "Proof of concept: ZDT4.mod"
author: "Jonathan Boualavong"
output: html_notebook
---

<!-- output:    -->
<!--   md_document: -->
<!--     variant: markdown_github -->

# Description
This notebook showcases the method below for finding acceptable suboptimal performance in the fourth rest function form Zitzler, Deb, and Thiele, 2000. 
The function is changed slightly to have a lower frequency in its cosine term to make it more reflective of physical systems.
The notebook will first test the algorithm using 3 inputs.

The intention is for this procedure to be applied to optimization problems where the input variables are discrete but unknown, such as selecting appropriate chemical compounds from a large set of options, and guide decisionmaking by indicating which variables are most important and what values it should have to yield optimal performance.

# Algorithm concept:
* I. Setup: find the Pareto frontier of the 2D optimization problem
1. Solve objective functions with a space filling method to obtain an initial set of data.
2. Use GPareto to find the Pareto front.
3. Calculatate the normalized distance in the objective space and f1/f2 prioritization of each point to the Pareto front. These two metrics will be used to establish the acceptable suboptimal performance and the relative importance of each input variable.

* II. Acceptable suboptimal performance (the "near-Pareto set")
4. Establish a selection criteria for acceptable suboptimal performance (eg. within some tolerance of the Pareto front).
5. Using Gaussian processes, create a new objective called the "sample utility" function that describes the probability of meeting the desired distance and objective function criteria, multiplied by the variance.
6. Sample new points iteratively by maximizing the sample utility function. Repeat until the computational budget has been expended or the sample utility function maximum drops below a specified threshold, often relative to first maximum.

* III. Feature importance of each input variable
7. Calculate the distance between each point and the Pareto front in both the input and objective space.
8. Compare the distance in the objective space to the Pareto front and the distance in only a single variable. The most important variable is that which has the largest correlation coefficient.
9. Calculate the conditional probability that a point will fall within the near-Pareto set given only information about the most important input variable.
10. Calculate the same conditional probability, but given the that the most important variable falls within its optimal range and the second most important variable is known.
11. Repeat step 10 by continuing to constrain the optimal range of the previous variables until all conditional probabilities have been found. This sequential analysis describes the characteristics of the most promising inputs for the near-Pareto set.

# Code
## 0. Initialization

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear the workspace and define the functions.

```{r Load Packages}
# Setup
rm(list = ls())
# Visualization
library(dplyr)
library(ggplot2)
library(patchwork)
# Parallel processing
library(parallel)
library(doParallel)
# Gaussian processes
library(GPareto)
library(DiceKriging)
library(DiceOptim)
# Optimization
library(GA)
```

The modified function ZDT4 takes N inputs, each on the domain of (0,1). The function is built into the GPareto package and does not need to be constructed explicitly.

## I. Setup: 
Find the Pareto frontier of the 2D optimization problem

The ZDT4 function has been modified slightly (changing the frequency of the cosine term) to have fewer local optima. This helps speed up calculations, as well as makes it more representative of the physical systems to test, which are not going to have very many rapid changes.

```{r}
ZDT4.mod = function (x) 
{
  if (is.null(dim(x))) {
    x <- matrix(x, nrow = 1)
  }
  n <- ncol(x)
  g <- 1 + 10 * (n - 1) + rowSums((x[, 2:n, drop = FALSE] * 
    0.5 - 0.25)^2 - 10 * cos(0.5 * pi * (x[, 2:n, drop = FALSE] * 
    10 - 5)))
  return(cbind(x[, 1], g * (1 - sqrt(x[, 1]/g))))
}

```

1. Solve objective functions with a space filling method to obtain an initial set of data.
The 2D function takes two inputs, defined $x_1$ and $x_2$, to produce two outputs $f_1$ and $f_2$. 
The domain of both $x_1$ and $x_2$ is [0,5]. The space-filling method here is a simple square grid construction.

```{r Grid Setup}
# Set up simple grid
sz = 5
x1.rng = seq(from = 0, to = 1, length.out = sz)
x2.rng = seq(from = 0, to = 1, length.out = sz)
x3.rng = seq(from = 0, to = 1, length.out = sz)
des.start = expand.grid(x1.rng, x2.rng, x3.rng)
des.start = des.start[,1:3]
names(des.start) = c('x1', 'x2', 'x3')

# Solve edge cases
Pareto.budget = 20
des.start = matrix(c(des.start$x1, des.start$x2, des.start$x3), ncol = 3, nrow = nrow(des.start))
res.start = ZDT4.mod(x = des.start)

```

2. Use GPareto to find the Pareto front.

GPareto uses Gaussian processes to approximate the Pareto frontier, defaulting to the SMS-EGO selection criterion.
The function produces both the Pareto frontier estimate and the set of iterations, which will both be used in subsequent steps.
To simplify computation time, the data are stored in .csv files so these variables do not need to be calculated with each attempt.

```{r GPareto Calculation}
res = easyGParetoptim(fn = ZDT4.mod, budget = Pareto.budget, lower = c(0, 0, 0), upper = c(1, 1, 1), 
                      par = des.start, value = res.start, ncores = 2)
plotGPareto(res)
# Format into dataframe for easier plotting
GPar.front = data.frame(x1 = res$par[,1], x2 = res$par[,2], x3 = res$par[,3], f1 = res$value[,1], f2 = res$value[,2])
GPar.all =  data.frame(x1 = res$history$X[,1], x2 = res$history$X[,2], x3 = res$history$X[,3], f1 = res$history$y[,1], f2 = res$history$y[,2])
GPar.all$order = c(rep(0, nrow(des.start)), seq(from = 1, to = Pareto.budget, by = 1))
rm(res)
write.csv(GPar.all, file = 'GPar_all_data.csv')
write.csv(GPar.front, file = 'GPar_fnt_data.csv')
```

3. Calculatate the normalized distance in the objective space and f1/f2 prioritization of each point to the Pareto front. These two metrics will be used to establish the acceptable suboptimal performance and the relative importance of each input variable.

Normalization is defined such that (0,0) is the utopia point and (1,0) and (0,1) are the single-objective optimizations. The prioitization is the angle $\theta$ made between the point in the normalized objective space and the x-axis, i.e. the axis of purely prioritizing objective 2. This angle is re-mapped to a percentage from 0 to 100% prioritization of objective 2. The distance between each point and the Pareto front is the distance in the normalized space

```{r Map to Normalized Objective Space}
GPar.all = read.csv(file = 'GPar_all_data.csv')
GPar.front = read.csv(file = 'GPar_fnt_data.csv')
Pareto.budget = nrow(GPar.all) - sz^3
# Saved data have an index
GPar.all = GPar.all[, !(names(GPar.all) %in% c("X"))]
GPar.front = GPar.front[, !(names(GPar.front) %in% c("X"))]
# Normalized objective functions
n.obj = function(GPar.data, GPar.front){
  # Given dataframes that describe the entire dataset and the front, find the normalized (x,y)
  # Objective functions are named 'f1' and 'f2'
  
  # Normalize the objective outputs so that the utopia point is (0,0) and the nadir point is (1,1)
  f1.up = GPar.front$f1[which.min(GPar.front$f2)]
  f2.up = GPar.front$f2[which.min(GPar.front$f1)]
  GPar.data$f1.norm = (GPar.data$f1 - min(GPar.front$f1))/(f1.up - min(GPar.front$f1))
  GPar.data$f2.norm = (GPar.data$f2 - min(GPar.front$f2))/(f2.up - min(GPar.front$f2))
  # In the event that the optimum is better:
  GPar.data$f1.norm[GPar.data$f1.norm < 0] = 0
  GPar.data$f2.norm[GPar.data$f2.norm < 0] = 0
  return(GPar.data)
}
# Run normalization
GPar.all = n.obj(GPar.data = GPar.all, GPar.front = GPar.front)
GPar.front = n.obj(GPar.data = GPar.front, GPar.front = GPar.front)
GPar.front = GPar.front[order(GPar.front$f1.norm),]

# Calculate theta according to the angle. Remap from [0, pi/2] to [0, 100] for simplicity
GPar.all$theta = atan(GPar.all$f2.norm/GPar.all$f1.norm)*180/pi*10/9

# Calculate the normalized distance
n.dist = function(f1.norm, f2.norm, GPar.front){
  # Given the normalized coordinates (f1.norm, f2.norm) and the Pareto frontier estimate,
  # find the distance along the constant f2/f1 ratio line
  
  # Determine the two points on the Pareto front that define the relevant segment
  GPar.front$theta = atan(GPar.front$f2.norm / GPar.front$f1.norm)
  ratio = atan(f2.norm/f1.norm)
  
  # Check if the angle is the same as a point on the Pareto front
  if(any(abs(ratio - GPar.front$theta) < 1e-5)){
    pos = which.min(abs(ratio - GPar.front$theta))
    Par.x = GPar.front$f1.norm[pos]
    Par.y = GPar.front$f2.norm[pos]
  } else{ # Otherwise, two points are needed for linear interpolation
    # Break the dataframe into theta above and below
    Par.above = GPar.front[GPar.front$theta - ratio > 0,]
    Par.below = GPar.front[GPar.front$theta - ratio < 0,]
    # Find the point closest to the angle
    pos.above = which.min(abs(ratio - Par.above$theta))
    pos.below = which.min(abs(ratio - Par.below$theta))
    # Linear interpolation
    ln.x = c(Par.above$f1.norm[pos.above], Par.below$f1.norm[pos.below])
    ln.y = c(Par.above$f2.norm[pos.above], Par.below$f2.norm[pos.below])
    slp = diff(ln.y)/diff(ln.x)
    # Find the point on the segment with the same angle, ie. the same ratio.
    # Solving with this constraint has analytical solution:
    Par.x = (ln.y[1] - slp*ln.x[1]) / (f2.norm/f1.norm - slp)
    Par.y = slp*(Par.x - ln.x[1]) + ln.y[1]
  }
  
  # Linear distance to the front is the difference between distances to the origin
  dist = sqrt(f1.norm^2 + f2.norm^2) - sqrt(Par.x^2 + Par.y^2)
  return(dist)
}

# Run distance calculations in parallel to speed up
cl <- makeCluster(2)
registerDoParallel(cl)
dist = foreach(row = 1:nrow(GPar.all)) %dopar%
  n.dist(f1.norm = GPar.all$f1.norm[row], f2.norm = GPar.all$f2.norm[row], GPar.front = GPar.front)
stopCluster(cl)
GPar.all$dist = unlist(dist)
rm(dist, cl)


# Save the starting data to test multiple types of acceptance criteria
write.csv(x = GPar.all, file = 'GPar_all_start.csv')
write.csv(x = GPar.front, file = 'GPar_fnt_start.csv')

```

Plot the contours of the original functions
```{r Plot Objective Functions}
# Fine grid spacing
sz.fine = 50
x1.rng = seq(from = 0, to = 1, length.out = sz.fine)
x2.rng = seq(from = 0, to = 1, length.out = sz.fine)
# x3.rng = seq(from = 0, to = 1, length.out = 5)
# x3.rng = unique(c(x3.rng, unique(GPar.front$x3)))
x3.rng = 0 # Simple slice for visualization
con.fine = expand.grid(x1.rng, x2.rng, x3.rng)
con.fine = con.fine[,1:3]
names(con.fine) = c('x1', 'x2', 'x3')

# Calculate
res = ZDT4.mod(x = as.matrix(con.fine))
con.fine$f1 = res[,1]; con.fine$f2 = res[,2]

ggplot() +
  geom_contour(data = con.fine, mapping = aes(x = x1, y = x2, z = f1, color = 'f1'), bins = 10) +
  geom_contour(data = con.fine, mapping = aes(x = x1, y = x2, z = f2, color = 'f2'), bins = 10) +
  labs(x = expression('x'[1]), y = expression('x'[2])) +
  geom_point(data = GPar.front, mapping = aes(x = x1, y = x2), color = "black") +
  geom_smooth(data = GPar.front, mapping = aes(x = x1, y = x2), color = "black", method = 'loess', formula = (y~x)) +
  scale_color_manual(name = 'Objective', values = c('f1' = 'red', 'f2' = 'blue'), 
                     labels = c('f1' = expression('F'[1]), 'f2' = expression('F'[2]))) +
  theme_classic() +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))

sz.fine = 100
x1.rng = seq(from = 0, to = 1, length.out = sz.fine)
x2.rng = seq(from = 0, to = 1, length.out = sz.fine)
x3.rng = seq(from = 0, to = 1, length.out = 9) # Simple slice for visualization
con.fine = expand.grid(x1.rng, x2.rng, x3.rng)
con.fine = con.fine[,1:3]
names(con.fine) = c('x1', 'x2', 'x3')

# Calculate
res = ZDT4.mod(x = as.matrix(con.fine))
con.fine$f1 = res[,1]; con.fine$f2 = res[,2]

ggplot() +
  geom_point(data = con.fine, 
                      mapping = aes(x = x1, y = x2, color = f2)) +
  labs(x = expression('x'[1]), y = expression('x'[2]*' or x'[3]), color = expression('F'[2])) +
  theme_classic() + facet_wrap(~x3) + 
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))

ggplot() +
  geom_point(data = con.fine, 
                      mapping = aes(x = x1, y = x2, color = f1)) +
  labs(x = expression('x'[1]), y = expression('x'[2]*' or x'[3]), color = expression('F'[1])) +
  theme_classic() + facet_wrap(~x3) + 
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))

rm(res, con.fine, x1.rng, x2.rng, x3.rng)
```

Three different selection criteria are to be tested: (1) normalized distance to the Pareto frontier, (2) independent threshold values of the two objective functions, (3) distance to the utopia point and relative prioritization. The hypervolume of the accepted region in the input space should be at least 5% of the total hypervolume. This requires some tuning to decide on what the selection criteria should be so a sufficiently large region is accepted.

This 5% cutoff will be assessed by Monte Carlo sampling, combined with a coarse 3x3 resolution grid to ensure all regions are sampled.

```{r Identifying cutoff criteria}
# Set up the grid
bounds = seq(from = 0, to = 1, length.out = 4)
# Collect an equal number of points from each grid section
nsamp = 5e2
test.samp = data.frame()
for(i in 1:3){
  for(j in 1:3){
    for(k in 1:3){
      next.grid = data.frame(x1 = runif(n = nsamp, min = bounds[i], max = bounds[i+1]),
                             x2 = runif(n = nsamp, min = bounds[j], max = bounds[j+1]),
                             x3 = runif(n = nsamp, min = bounds[k], max = bounds[k+1]))
      test.samp = rbind(test.samp, next.grid)
    }
  }
}

# Calculate the function evaluations
res = ZDT4.mod(x = as.matrix(test.samp[,c('x1', 'x2', 'x3')]))
test.samp$f1 = res[,1]; test.samp$f2 = res[,2]
# Normalized variables
test.samp = n.obj(GPar.data = test.samp, GPar.front = GPar.front)

# Calculate theta according to the angle. Remap from [0, pi/2] to [0, 100] for simplicity
test.samp$theta = atan(test.samp$f2.norm/test.samp$f1.norm)*180/pi*10/9

# Distance to the Pareto front
cl <- makeCluster(2)
registerDoParallel(cl)
dist = foreach(row = 1:nrow(test.samp)) %dopar%
  n.dist(f1.norm = test.samp$f1.norm[row], f2.norm = test.samp$f2.norm[row], GPar.front = GPar.front)
stopCluster(cl)
test.samp$dist = unlist(dist)
rm(dist, cl)

# Fraction meeting dist < specific value
dist.check = data.frame(x = seq(from = 0, to = 5, length.out = 20),
                        delta = 0, cutof = 0, radan = 0)
for(i in 1:nrow(dist.check)){
  bound = dist.check$x[i]
  dist.check$delta[i] = nrow(filter(test.samp, dist <= bound))/nrow(test.samp)
  dist.check$cutof[i] = nrow(filter(test.samp, f1.norm <= bound, f2.norm <= bound))/nrow(test.samp)
  dist.check$radan[i] = nrow(filter(test.samp, sqrt(f1.norm^2 + f2.norm^2) <= bound & theta > 20))/nrow(test.samp)
  
}
sz = 2.5
dist.check
ggplot(dist.check) +
  geom_point(mapping = aes(x = x, y = delta, color = 'delta', shape = 'delta'), size = sz) +
  geom_point(mapping = aes(x = x, y = cutof, color = 'cutof', shape = 'cutof'), size = sz) +
  geom_point(mapping = aes(x = x, y = radan, color = 'radan', shape = 'radan'), size = sz) +
  scale_color_manual(values = c('delta' = 'red', 'cutof' = 'blue', 'radan' = 'green3'),
                     labels = c('delta' = 'P.Dist', 'cutof' = 'Cutoff', 'radan' = 'U.Dist'), 
                     name = '') +
  scale_shape_manual(values = c('delta' = 1, 'cutof' = 2, 'radan' = 3),
                     labels = c('delta' = 'P.Dist', 'cutof' = 'Cutoff', 'radan' = 'U.Dist'),
                     name = '') +
  labs(x = 'Cutoff Value', y = 'Accepted Fraction')

rm(bounds, nsamp, test.samp, sz, dist.check, next.grid, res)

```
Based on this Monte Carlo estimate, the cutoff value should be approximately 2 for all 3 criteria to guarantee at least 5% of the total hypervolume space is accepted.

Plot the full dataset in the objective space
```{r Visualize GPareto and Normalization, fig.width=6, fig.height=6}
gplt.GPar = ggplot() +
  geom_hline(yintercept = 0, linetype = 'dotted', color = 'black') + geom_vline(xintercept = 0, linetype = 'dotted', color = 'black') +
  geom_line(data = GPar.front, mapping = aes(x = f1, y = f2), color = "black") +
  geom_point(data = GPar.all, mapping = aes(x = f1, y = f2, color = (order > 0), 
                                            shape = (dist == 0)), size = 2) +
  labs(x = "Function 1", y = "Function 2", color = "") +  
  scale_color_discrete(labels = c('Starting Data', 'Pareto Search'), breaks = c(FALSE, TRUE)) +
  scale_shape_discrete(labels = c('Pareto frontier'), breaks = c(TRUE)) +
  theme_classic() + theme(legend.position = c(0.85, 0.85), legend.background = element_rect(fill = 'white'), 
                          legend.title = element_blank())

gplt.Norm = ggplot() +
  geom_hline(yintercept = 0, linetype = 'dotted', color = 'black') + geom_vline(xintercept = 0, linetype = 'dotted', color = 'black') +
  geom_line(data = GPar.front, mapping = aes(x = f1.norm, y = f2.norm), color = "black") +
  geom_point(data = GPar.all, mapping = aes(x = f1.norm, y = f2.norm, color = (order > 0),
                                            shape = (dist == 0)), size = 2) +
  labs(x = "Normalized Function 1", y = "Normalized Function 2", color = "") +  
  scale_color_discrete(labels = c('Starting Data', 'Pareto Search'), breaks = c(FALSE, TRUE)) +
  scale_shape_discrete(labels = c('Pareto frontier'), breaks = c(TRUE)) +
  guides(color = FALSE, shape = FALSE) +
  theme_classic() + theme(legend.position = c(0.85, 0.85), legend.background = element_rect(fill = 'white'),
                          legend.title = element_blank())

gplt.GPar / gplt.Norm
rm(gplt.GPar, gplt.Norm)
```

## II. Acceptable suboptimal performance (the "near-Pareto set")
4. Establish a selection criteria for acceptable suboptimal performance (eg. within some tolerance of the Pareto front).

For this example, defines $\delta$ as the distance between the point and the point on the Pareto frontier with the same value of theta. Accept only points with $\delta < 2$.

```{r Load data: Accept Distance less than 2}
# Load data
GPar.all = read.csv(file = 'GPar_all_start.csv')
GPar.front = read.csv(file = 'GPar_fnt_start.csv')

# Remove leading indices: check if the first name is x1
while(names(GPar.all)[1] != 'x1'){
  GPar.all = GPar.all[,2:length(names(GPar.all))]
}
while(names(GPar.front)[1] != 'x1'){
  GPar.front = GPar.front[,2:length(names(GPar.front))]
}

```

5. Using Gaussian processes, create a new objective called the "sample utility" function that describes the probability of meeting the desired distance and objective function criteria, multiplied by the variance.

The sample utility function prioritizes points that are likely to describe the boundary (normalized distance equal to 1) with the greatest model uncertainty at the time. 
When the point is sampled, this means information gained is maximized. 
Points on the boundary have intermediate acceptance probabilities, ie. close to 0.5, while points with the greatest model uncertainty have the greatest standard error. 
Therefore, the utility function can be estimated as the product of the standard error, the probability of being accepted, and the probability of being rejected.

```{r Functions: Iterative Sampling, message=FALSE, warning=FALSE}
fill.sample.mod = function(GPar.data, input.name, output.name){
  # Calculate the GP model to use. 
  # Using the km function, but applies checks on the system to make sure that 
  # the model uncertainty matches expectations based on GP, ie. it did not
  # fail to converge.
  
  # Based on testing, the model is bad when the 10% percentile and 90% percentile 
  # of the standard deviation are of the same order of magnitude. This is easiest
  # checked if the difference between the 10th and 90th percentile
  # is larger than the difference between the 25th and 75th.
  pt10 = 1; pt90 = 1; pt25 = 1; pt75 = 1
  while(log10(pt90/pt10) <= log10(pt75/pt25)){
    mod.out = km(design = GPar.data[, input.name], response = GPar.data[, output.name], 
                 covtyp = 'gauss', # Gaussian uncertainty
                 optim.method = 'gen', # Genetic algorithm optimization
                 control = list(trace = FALSE, # Turn off tracking to simplify output
                                pop.size = 50), # Increase robustness
                 nugget = 1e-6, # Avoid eigenvalues of 0
                 )
    
    # Randomly sample 1000 points from the search space.
    pt = 1000; i = 1
    lims = range(GPar.data[,input.name[i]])
    samp = data.frame(runif(n = pt, min = lims[1], max = lims[2]))
    for(i in 2:length(input.name)){
      lims = range(GPar.data[,input.name[i]])
      samp[,i] = runif(n = pt, min = lims[1], max = lims[2])
    }
    names(samp) = input.name
    
    # Find model output to find the percentile ranks for this iteration
    res = predict(object = mod.out, newdata = samp, type = 'UK')
    pt10 = quantile(res$sd, 0.10); pt90 = quantile(res$sd, 0.90)
    pt25 = quantile(res$sd, 0.25); pt75 = quantile(res$sd, 0.75)
  }
  return(mod.out)
}

fill.sample.obj = function(x, model){
  # Given data that contains: function evaluations (f1, f2) at inputs (x1, x2), and the normalized distance of (f1, f2) to the Pareto front
  # the function will output the objective function evaluated at x = (x1, x2)
  
  # Evaluate the Kriging model function at x 
  res = predict(object = model, newdata = data.frame(x1 = x[1], x2 = x[2], x3 = x[3]), type = 'UK')
  
  # Probability distribution fits a Gaussian distribution
  prob = pnorm(q = 0, mean = res$mean - 2, sd = res$sd)

  # Objective result
  return(res$sd*(prob*(1-prob) + 0.25/9))
}

# Check to make sure that the front estimate is correct after sampling
fill.sample.front.check = function(point.new, front.old){
  # Only need x and f variables
  front.old = front.old[,names(point.new)]
  # Check all possible points, assuming multiple are screened at once
  for(i in 1:nrow(point.new)){
    # If it dominates an existing Pareto point:
    front.old[front.old$f1 > point.new$f1[i] & front.old$f2 > point.new$f2[i]] = NULL
    # If it is non-dominating but not strictly worse
    pos1 = (front.old$f1 < point.new$f1[i] & front.old$f2 > point.new$f2[i]) | 
      (front.old$f1 > point.new$f1[i] & front.old$f2 < point.new$f2[i])
    if(all(pos1)){front.old = rbind(front.old, point.new)}
  }
  # Re-calculate the normalization
  front.new = n.obj(front.old, front.old)
  return(front.new)
}

```

Visualize the first iteration to show that it actually samples the point that is most useful
```{r Iteration 1: Distance less than 1}
# Search for the first point
mod.dist = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'dist')
GA.pred = ga(type = 'real-valued',
             fitness = function(x){fill.sample.obj(x, model = mod.dist)},
             lower = c(0, 0, 0), upper = c(1, 1, 1),
             popSize = 50, maxiter = 50, run = 10, monitor = FALSE,
             parallel = 2)
# Next point to sample is the solution to this optimization
point.next = GA.pred@solution[1,]
GPar.new = data.frame(x1 = point.next[1], x2 = point.next[2], x3 = point.next[3])
res = ZDT4.mod(x = as.matrix(GPar.new))
GPar.new$f1 = res[,1]; GPar.new$f2 = res[,2]
GPar.front = fill.sample.front.check(point.new = GPar.new, front.old = GPar.front)
  
# Fill in the remaining calculations: normalized outputs, distance, theta, order
GPar.new = n.obj(GPar.data = GPar.new, GPar.front = GPar.front)
GPar.new$theta = atan(GPar.new$f2.norm/GPar.new$f1.norm)*180/pi*10/9
cl <- makeCluster(2)
registerDoParallel(cl)
dist = foreach(row = 1:nrow(GPar.new)) %dopar%
  n.dist(f1.norm = GPar.new$f1.norm[row], f2.norm = GPar.new$f2.norm[row], GPar.front = GPar.front)
stopCluster(cl)
GPar.new$dist = unlist(dist)
GPar.new$order = max(GPar.all$order) + 1

# The cutoff point for the loop is 20 additional points or when the fitness value is less than half of this starting fitness value
start.fit = max(GA.pred@fitness)
# Store first point for plotting
GPar.new1 = GPar.new
rm(dist)

# Store the initial mod.dist for later
mod.dist.init = mod.dist
```

```{r}
lower = c(0, 0.3, 0); upper = c(1, 0.7, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x3 = c(GPar.new$x3),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x2 = c(seq(from = lower[3], to = upper[3], length.out = 50)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x3', 'x2')
# Apply Kriging function of distance
res = predict(object = mod.dist.init, newdata = fine.grid, type = "UK")
fine.grid$dist.mean = res$mean
fine.grid$dist.sd = res$sd

# Probability that the distance is less than 1
fine.grid$dist.p1 = pnorm(q = 0, mean = fine.grid$dist.mean - 2, sd = fine.grid$dist.sd)
fine.grid$uncert = fine.grid$dist.p1*(1-fine.grid$dist.p1)+1e-10
ncolor = 7
g1 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = uncert, z = uncert), 
                      breaks = seq(from = 0, to = 0.25, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = '', y = 'x2', title = 'Uncertainty')
rng = range(fine.grid$dist.sd)
g2 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = dist.sd, z = dist.sd), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = 'x1', y = '', title = 'Information Gain')
rng = range(fine.grid$dist.sd*fine.grid$uncert)
g3 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = uncert*dist.sd, z = uncert*dist.sd), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr",  name = '')  +
  labs(x = '', y = '', title = 'Sample Utility')
(g1 + guides(fill = FALSE)) + (g2 + guides(fill = FALSE)) + g3

## x3 slices
lower = c(0, 0.3, 0); upper = c(1, 0.7, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x2 = c(GPar.new$x2),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x3 = c(seq(from = lower[3], to = upper[3], length.out = 50)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x2', 'x3')
# Apply Kriging function of distance
res = predict(object = mod.dist.init, newdata = fine.grid, type = "UK")
fine.grid$dist.mean = res$mean
fine.grid$dist.sd = res$sd

# Probability that the distance is less than 1
fine.grid$dist.p1 = pnorm(q = 0, mean = fine.grid$dist.mean - 2, sd = fine.grid$dist.sd)
fine.grid$uncert = fine.grid$dist.p1*(1-fine.grid$dist.p1)+1e-10
ncolor = 7
g1 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = uncert, z = uncert), 
                      breaks = seq(from = 0, to = 0.25, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = '', y = 'x3', title = 'Uncertainty')
rng = range(fine.grid$dist.sd)
g2 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = dist.sd, z = dist.sd), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = 'x1', y = '', title = 'Information Gain')
rng = range(fine.grid$dist.sd*fine.grid$uncert)
g3 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = uncert*dist.sd, z = uncert*dist.sd), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr", name = '')  +
  labs(x = '', y = '', title = 'Sample Utility')

(g1 + guides(fill = FALSE)) + (g2 + guides(fill = FALSE)) + g3

rm(g1, g2, g3, fine.grid)
```

6. Sample new points iteratively by maximizing the sample utility function. Repeat until the computational budget has been expended or a stop criteria is met.

A typical stop criteria is based on the hypervolume fraction that is uncertain, i.e. an acceptance probability between 0.25 and 0.75. However, as the number of input variables increases, the number of sampled points required for an accurate Monte Carlo estimate increases dramatically. Instead, a single point criteria is more useful; in this case, the metric is the maximum sample utility in the optimization function. When the value drops by 2 orders of magnitude, then the next point is not likely to provide much improvement.

```{r Iteration loop: Accept distance less than 1, message=FALSE, warning=FALSE}
budget = 20

next.fit = start.fit
while(next.fit > start.fit*0.01 & max(GPar.all$order) < budget+Pareto.budget){
  # Add the  new point to the dataset
  GPar.all = rbind(GPar.all, GPar.new)
  
  # Create new Kriging model
  mod.dist = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'dist')
  
  # Run the optimization to find the best point
  GA.pred = ga(type = 'real-valued',
               fitness = function(x){fill.sample.obj(x, model = mod.dist)},
               lower = c(0, 0, 0), upper = c(1, 1, 1),
               popSize = 50, maxiter = 50, run = 10, monitor = FALSE,
               parallel = 2)
  
  # Next point to sample is the solution to this optimization. 
  # Account for the possibility that the genetic algorithm converges on multiple equivalent points
  point.next = GA.pred@solution[1,]
  
  # Find values of the selected point
  GPar.new = data.frame(x1 = point.next[1], x2 = point.next[2], x3 = point.next[3])
  res = ZDT4.mod(x = as.matrix(GPar.new))
  GPar.new$f1 = res[,1]; GPar.new$f2 = res[,2]
  GPar.front = fill.sample.front.check(point.new = GPar.new, front.old = GPar.front)

  # Fill in the remaining calculations: normalized outputs, distance, theta, order
  GPar.new = n.obj(GPar.data = GPar.new, GPar.front = GPar.front)
  cl <- makeCluster(2)
  registerDoParallel(cl)
  dist = foreach(row = 1:nrow(GPar.new)) %dopar%
    n.dist(f1.norm = GPar.new$f1.norm[row], f2.norm = GPar.new$f2.norm[row], GPar.front = GPar.front)
  stopCluster(cl)
  GPar.new$dist = unlist(dist)
  GPar.new$theta = atan(GPar.new$f2.norm/GPar.new$f1.norm)*180/pi*10/9
  GPar.new$order = max(GPar.all$order) + 1
  
  # The cutoff point for the loop is 20 additional points or when the 
  # fitness value is less than 1% of this starting fitness value
  next.fit = max(GA.pred@fitness)
}

GPar.all = rbind(GPar.all, GPar.new)
# Save the data for later
write.csv(GPar.all, 'GPar_Accept_Delta1.csv')

rm(point.next)
```

```{r}
# Plot results on top of the most recent Kriging model
GPar.all = read.csv(file = 'GPar_Accept_Delta1.csv')
mod.dist = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'dist')

lower = c(0, 0.3, 0); upper = c(1, 0.7, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x3 = c(GPar.new$x3),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x2 = c(seq(from = lower[3], to = upper[3], length.out = 50)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x3', 'x2')
# Apply Kriging function of distance
res = predict(object = mod.dist, newdata = fine.grid, type = "UK")
fine.grid$dist.mean = res$mean
fine.grid$dist.sd = res$sd

# Probability that the distance is less than 1
fine.grid$dist.p1 = pnorm(q = 0, mean = fine.grid$dist.mean - 2, sd = fine.grid$dist.sd)
fine.grid$uncert = fine.grid$dist.p1*(1-fine.grid$dist.p1)+1e-10
ncolor = 7
g1 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = uncert, z = uncert), 
                      breaks = seq(from = 0, to = 0.25, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x2, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = '', y = 'x2', title = 'Uncertainty')
rng = range(fine.grid$dist.sd)
g2 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = dist.sd, z = dist.sd), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x2, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = 'x1', y = '', title = 'Information Gain')
rng = range(fine.grid$dist.sd*fine.grid$uncert)
g3 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = uncert*dist.sd, z = uncert*dist.sd), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x2, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr",  name = '')  +
  labs(x = '', y = '', title = 'Sample Utility')
(g1 + guides(fill = FALSE)) + (g2 + guides(fill = FALSE)) + g3

## x3 slices
lower = c(0, 0.3, 0); upper = c(1, 0.7, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x2 = c(GPar.new$x2),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x3 = c(seq(from = lower[3], to = upper[3], length.out = 50)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x2', 'x3')
# Apply Kriging function of distance
res = predict(object = mod.dist, newdata = fine.grid, type = "UK")
fine.grid$dist.mean = res$mean
fine.grid$dist.sd = res$sd

# Probability that the distance is less than 1
fine.grid$dist.p1 = pnorm(q = 0, mean = fine.grid$dist.mean - 2, sd = fine.grid$dist.sd)
fine.grid$uncert = fine.grid$dist.p1*(1-fine.grid$dist.p1)+1e-10
ncolor = 7
g1 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = uncert, z = uncert), 
                      breaks = seq(from = 0, to = 0.25, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x3, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = '', y = 'x3', title = 'Uncertainty')
rng = range(fine.grid$dist.sd)
g2 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = dist.sd, z = dist.sd), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x3, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = 'x1', y = '', title = 'Information Gain')
rng = range(fine.grid$dist.sd*fine.grid$uncert)
g3 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = uncert*dist.sd, z = uncert*dist.sd), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x3, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr", name = '')  +
  labs(x = '', y = '', title = 'Sample Utility')

(g1 + guides(fill = FALSE)) + (g2 + guides(fill = FALSE)) + g3

rm(g1, g2, g3, fine.grid)

```
## III. Feature importance of each input variable
7. Calculate the distance between each point and the Pareto front in both the input and objective space.
8. Compare the distance in the objective space to the Pareto front and the distance in only a single variable. The most important variable is that which has the largest correlation coefficient.

```{r Feature Importance: Correlation Coefficient and Slope}
# Load data
GPar.all = read.csv(file = 'GPar_Accept_Delta1.csv')
GPar.front = read.csv(file = 'GPar_fnt_start.csv')
# Remove leading indices: the names are:
nm = c("x1",  "x2", "x3", "f1", "f2", "order",  "f1.norm", "f2.norm", "dist", "theta")
GPar.all = GPar.all[,nm]
nm = c("x1",  "x2", "x3", "f1", "f2",  "f1.norm", "f2.norm")
GPar.front = GPar.front[,nm]

# Define the process used to collect the point
GPar.all$proc = 'Initial'
GPar.all$proc[GPar.all$order > 0] = 'Pareto'
GPar.all$proc[GPar.all$order > Pareto.budget] = 'Post'
# Break up the prioritization into favoring f1, f2, or a balance of the two
GPar.all$region = "f1"
GPar.all$region[GPar.all$theta < 200/3] = "50:50"
GPar.all$region[GPar.all$theta < 100/3] = "f2"

pt.size = 3
g1 = ggplot() +
  geom_point(data = filter(GPar.all, dist > 1), mapping = aes(x = theta, y = x1, shape = proc), color = 'red', size = pt.size, alpha = 0.5) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x1), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x1, color = dist, shape = proc), size = pt.size) +
  labs(x = "", y = expression("x"[1]), color = "Distance:\nObjective\nSpace") +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(shape = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g2 = ggplot() +
  geom_point(data = filter(GPar.all, dist >  1), mapping = aes(x = theta, y = x2, shape = proc), color = 'red', size = pt.size, alpha = 0.5) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x2), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x2, color = dist, shape = proc), size = pt.size) +
  labs(x = "Trade-Off", y = expression("x"[2]), color = "", shape = 'Collection\nProcess') +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(color = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g3 = ggplot() +
  geom_point(data = filter(GPar.all, dist >  1), mapping = aes(x = theta, y = x3, shape = proc), color = 'red', size = pt.size, alpha = 0.5) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x3), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x3, color = dist, shape = proc), size = pt.size) +
  labs(x = "Trade-Off", y = expression("x"[3]), color = "", shape = 'Collection\nProcess') +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(color = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g1 / g2 / g3

# Approximate the Pareto front with a smoothed line using a Savitzky-Golay filter
Pfront.x1 = loess(x1 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                                x1 = filter(GPar.all, dist == 0)$x1))
Pfront.x2 = loess(x2 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                               x2 = filter(GPar.all, dist == 0)$x2))
Pfront.x3 = loess(x3 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                               x3 = filter(GPar.all, dist == 0)$x3))

# Store the information in a dataframe for visualization
plt = data.frame(theta = seq(from = 0, to = 100, length.out = 100))
res1 = predict(object = Pfront.x1, newdata = plt)
res2 = predict(object = Pfront.x2, newdata = plt)
res3 = predict(object = Pfront.x3, newdata = plt)
plt$x1 = unname(res1); plt$x2 = unname(res2); plt$x3 = unname(res3)
# Check the Savitzky–Golay filter smoothing quality
gx1 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x1)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x1))
gx2 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x2)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x2))
gx3 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x3)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x3))
gx1 / gx2 / gx3

# Apply the model to find the linear distance (regression)
GPar.all$x1.loess.Err = abs(GPar.all$x1 - predict(object = Pfront.x1, newdata = GPar.all$theta))
GPar.all$x2.loess.Err = abs(GPar.all$x2 - predict(object = Pfront.x2, newdata = GPar.all$theta))
GPar.all$x3.loess.Err = abs(GPar.all$x3 - predict(object = Pfront.x3, newdata = GPar.all$theta))

# Calculate the correlation coefficient of the log(objective distance) with the linear distance
x1.cor = cor(x = filter(GPar.all, dist > 0)$x1.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
x2.cor = cor(x = filter(GPar.all, dist > 0)$x2.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
x3.cor = cor(x = filter(GPar.all, dist > 0)$x3.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
# Calculate the slope of the linear relationship
x1.slp = lm((dist) ~ x1.loess.Err, data = filter(GPar.all, dist > 0))
x2.slp = lm((dist) ~ x2.loess.Err, data = filter(GPar.all, dist > 0))
x3.slp = lm((dist) ~ x3.loess.Err, data = filter(GPar.all, dist > 0))
x1.slp = unname(x1.slp$coefficients[2]); x2.slp = unname(x2.slp$coefficients[2])
x3.slp = unname(x3.slp$coefficients[2])

sz = 3
# Store information in a dataframe for plotting
GPar.cor.plt = data.frame(obj.dist = rep(GPar.all$dist, 3),
                          inp.dist = c(GPar.all$x1.loess.Err, GPar.all$x2.loess.Err, GPar.all$x3.loess.Err),
                          var = c(rep('x1', nrow(GPar.all)), rep('x2', nrow(GPar.all)), rep('x3', nrow(GPar.all))),
                          region = rep(GPar.all$region, 3),
                          val = c(GPar.all$x1, GPar.all$x2, GPar.all$x3))
var.labs <- c(paste('x1, r = ', round(x1.cor, 3), '; slope = ', round(x1.slp, 3)), 
              paste('x2, r = ', round(x2.cor, 3), '; slope = ', round(x2.slp, 3)),
              paste('x3, r = ', round(x3.cor, 3), '; slope = ', round(x3.slp, 3)))
names(var.labs) <- c("x1", "x2", "x3")

ggplot(GPar.cor.plt) +
  geom_point(mapping = aes(x = inp.dist, y = (obj.dist), shape = region, color = val), size = sz) +
  facet_grid(~var, labeller = labeller(var = var.labs)) + 
  labs(x = 'Distance: Input Space', y = expression('log'[10]*' Distance: Objective Space'), shape = 'Priority',
       color = 'Input Value')

rm(g1, g2, g3, gx1, gx2, gx3, Pfront.x1, Pfront.x2, Pfront.x3, plt, GPar.cor.plt)
```

Based on this regression-based interpretation of the ranking, it appears that x3 is more important than x2, which is more important that x1. While one would expect x2 and x3 to be of equivalent importance, it is likely that the exact points that were sampled biased more towards showing a trend with x3 over x2.

9. Calculate the conditional probability that a point will fall within the near-Pareto set given only information about the most important input variable.

From the above calculations, the most important variable is x1, as it has a stronger relationship between distance in the objective space and distance in the input space (i.e. a larger perturbation in the input will lead to a less optimal result).

For the purposes of illustration, both P[accept | $x_1$] and P[accept | $x_2$] will be shown to show how the regression is consistent with the probabilities.
The conditional probability is calculated by marginalization of the GP probabilities. From the GP, the value of P[accept | $x_1, x_2$] can be calculated, and the relationship between P[accept | $x_1, x_2$] and  P[accept | $x_1$] is the integral:

P[accept | $x_1$] = integral( P[accept | $x_1, x_2$]  P[$x_2$] $dx_2$ )

In the absence of data to inform the distribution of $x_2$, this distribution is set as a uniform distribution on the range used in the optimization.

```{r Marginalization}
# Use the final GP model with the full dataset
mod.dist = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'dist')

# Obtain marginalized probabilities with a fine resolution grid (50 points). Calculate the integral with a Monte Carlo sampling of 500 samples each.
resolution = 50; MCsamp = 1500
x1.rng = range(GPar.all$x1); x2.rng = range(GPar.all$x2); x3.rng = range(GPar.all$x3)
x1.seq = seq(from = min(x1.rng), to = max(x1.rng), length.out = resolution)
x2.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)
x3.seq = seq(from = min(x3.rng), to = max(x3.rng), length.out = resolution)

Infer.x1 = data.frame(); Infer.x2 = data.frame(); Infer.x3 = data.frame()

for(i in 1:resolution){
  # x1
  fill.frame = data.frame(x1 = x1.seq[i], x2 = runif(n = MCsamp, min = min(x2.rng), max = max(x2.rng)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res = predict(object = mod.dist, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res$mean - 2, sd = res$sd)
  Infer.x1 = rbind(Infer.x1, data.frame(x = x1.seq[i], prob = mean(fill.frame$p.del1), var = 'x1', cond = 'none'))
  
  # x2
  fill.frame = data.frame(x2 = x2.seq[i], x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res = predict(object = mod.dist, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res$mean - 2, sd = res$sd)
  Infer.x2 = rbind(Infer.x2, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'none'))
  
  # x3
  fill.frame = data.frame(x3 = x3.seq[i], x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)),
                          x2 = runif(n = MCsamp, min = min(x2.rng), max = max(x2.rng)))
  res = predict(object = mod.dist, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res$mean - 2, sd = res$sd)
  Infer.x3 = rbind(Infer.x3, data.frame(x = x3.seq[i], prob = mean(fill.frame$p.del1), var = 'x3', cond = 'none'))
}

ggplot() +
  geom_path(data = Infer.x1, mapping = aes(x = x, y = prob, color = var)) +
  geom_path(data = Infer.x2, mapping = aes(x = x, y = prob, color = var)) +
  geom_path(data = Infer.x3, mapping = aes(x = x, y = prob, color = var)) +
  labs(x = expression('x'), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 2')) +
  scale_color_manual(name = 'Variable', values = c('x1' = 'red', 'x2' = 'blue', 'x3' = 'purple'), 
                    labels = c('x1' = expression('x'[1]), 'x2' = expression('x'[2]),'x3' = expression('x'[3]))) +
  theme_bw()
```

Consistent with the correlation coefficients, the probability of acceptance when only $x_2$ or $x_3$ is known has a higher and sharper peak than $x_1$. The reason for $x_3$'s relative dominance is clear here: the sampling for $x_3$ apparently did not capture the local minima, whereas it did capture the local minima from $x_2$.

10. Calculate the same conditional probability, but given the that the most important variable falls within its optimal range and the second most important variable is known.
11. Repeat step 10 by continuing to constrain the optimal range of the previous variables until all conditional probabilities have been found. This sequential analysis describes the characteristics of the most promising inputs for the near-Pareto set.

For the 3-input set, there are 6 possible pairwise conditionals, where one variable is known precisely and the other falls within its single-variable optimal range, eg. accept | $x_2, x_1 = x_{1,opt}$

For the purposes of comparison, the 'best' permutation (optimize x3, then x2, then x1) will be compared to the worst permutation (optimize x1, then x2, then x3). These orders are based on the importance rankings.


```{r Partial Conditional Probabilities}
# Determining the ranges
# Function to find the optimal range given the probability of acceptance
p.lims = function(data.prob, p.target){
  # data.prob is a dataframe with variables x and prob, which are the values and probability of acceptance
  
  # Limits are the range where the probability is at least half the maximim
  # p.target = 0.5*max(data.prob$prob)
  
  # Initial limits
  x.lims = range(filter(data.prob, prob >= p.target)$x)
  
  # Linear interpolate to find the proper point, assuming that the limit is not already the minimum possible value
  if(x.lims[1] > min(data.prob$x)){
    pos = which.min(abs(data.prob$x - x.lims[1]))
    sub = data.prob[c(pos-1, pos), ]
    mod = lm(x~prob, data = sub)
    res = predict(object = mod, newdata = data.frame(prob = p.target))
    x.lims[1] = res
  }
  if(x.lims[2] < max(data.prob$x)){
    pos = which.min(abs(data.prob$x - x.lims[2]))
    sub = data.prob[c(pos, pos+1), ]
    mod = lm(x ~ prob, data = sub)
    res = predict(object = mod, newdata = data.frame(prob = p.target))
    x.lims[2] = res
    rm(mod)
  }
  return(x.lims)
}
x1.lims = p.lims(data.prob = Infer.x1, p.target = 0.5*max(Infer.x1$prob))
x3.lims = p.lims(data.prob = Infer.x3, p.target = 0.5*max(Infer.x3$prob))

## Given that x1 or x3 is optimal, find the next variable in the series: x2
resolution = 50; MCsamp = 1500
x2.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)

# Single conditional: x2|x1 or x2|x3
Infer.x2.x1 = data.frame(); Infer.x2.x3 = data.frame()

for(i in 1:resolution){
  # x2 | x1
  fill.frame = data.frame(x2 = x2.seq[i], x1 = runif(n = MCsamp, min = min(x1.lims), max = max(x1.lims)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res = predict(object = mod.dist, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res$mean - 2, sd = res$sd)
  Infer.x2.x1 = rbind(Infer.x2.x1, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'x1'))
  # x2 | x3
  fill.frame = data.frame(x2 = x2.seq[i], x3 = runif(n = MCsamp, min = min(x3.lims), max = max(x3.lims)),
                          x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)))
  res = predict(object = mod.dist, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res$mean - 2, sd = res$sd)
  Infer.x2.x3 = rbind(Infer.x2.x3, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'x3'))
}

ggplot(rbind(Infer.x2.x3, Infer.x2.x1)) +
  geom_path(mapping = aes(x = x, y = prob, color = cond)) +
  labs(x = expression('x'[2]), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'),
       color = 'Given optimal') +
  theme_bw()

# Instead of a simple range, the multimodal peaks of these probability curves mean a simple min/max bound can be used. While a nearest-neighbor approximation would work, a faster solution is to find 3 separate ranges.
x2.lims.x3.rng1 = p.lims(data.prob = filter(Infer.x2.x3, x < 0.25), 
                         p.target = max(Infer.x2.x3$prob)*0.5)
x2.lims.x3.rng2 = p.lims(data.prob = filter(Infer.x2.x3, x > 0.25, x < 0.75), 
                         p.target = max(Infer.x2.x3$prob)*0.5)
x2.lims.x3.rng3 = p.lims(data.prob = filter(Infer.x2.x3, x > 0.75), 
                         p.target = max(Infer.x2.x3$prob)*0.5)
x2.lims.x1.rng1 = p.lims(data.prob = filter(Infer.x2.x1, x < 0.25), 
                         p.target = max(Infer.x2.x1$prob)*0.5)
x2.lims.x1.rng2 = p.lims(data.prob = filter(Infer.x2.x1, x > 0.25, x < 0.75), 
                         p.target = max(Infer.x2.x1$prob)*0.5)
x2.lims.x1.rng3 = p.lims(data.prob = filter(Infer.x2.x1, x > 0.75), 
                         p.target = max(Infer.x2.x1$prob)*0.5)
# The number of points to collect from each range is proportional to their relative widths

## Given that x1 or x3 is optimal, find the next variable in the series: x2
# resolution = 50; MCsamp = 1500
MCsamp.x2.x3.rng1 = round(1500*diff(x2.lims.x3.rng1)/
                            (diff(x2.lims.x3.rng1) + diff(x2.lims.x3.rng2) + diff(x2.lims.x3.rng3)))
MCsamp.x2.x3.rng2 = round(1500*diff(x2.lims.x3.rng2)/
                            (diff(x2.lims.x3.rng1) + diff(x2.lims.x3.rng2) + diff(x2.lims.x3.rng3)))
MCsamp.x2.x3.rng3 = 1500 - MCsamp.x2.x3.rng1 - MCsamp.x2.x3.rng2
MCsamp.x2.x1.rng1 = round(1500*diff(x2.lims.x1.rng1)/
                            (diff(x2.lims.x1.rng1) + diff(x2.lims.x1.rng2) + diff(x2.lims.x1.rng3)))
MCsamp.x2.x1.rng2 = round(1500*diff(x2.lims.x1.rng2)/
                            (diff(x2.lims.x1.rng1) + diff(x2.lims.x1.rng2) + diff(x2.lims.x1.rng3)))
MCsamp.x2.x1.rng3 = 1500 - MCsamp.x2.x1.rng1 - MCsamp.x2.x1.rng2

x1.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)
x3.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)

# Single conditional: x2|x1 or x2|x3
Infer.x3.x2.x1 = data.frame(); Infer.x1.x2.x3 = data.frame()
for(i in 1:resolution){
  # x3 | x2, x1
  x2.fill = c(runif(n = MCsamp.x2.x1.rng1, min = min(x2.lims.x1.rng1), max = max(x2.lims.x1.rng1)),
              runif(n = MCsamp.x2.x1.rng2, min = min(x2.lims.x1.rng2), max = max(x2.lims.x1.rng2)),
              runif(n = MCsamp.x2.x1.rng3, min = min(x2.lims.x1.rng3), max = max(x2.lims.x1.rng3)))
  fill.frame = data.frame(x2 = x2.fill, x1 = runif(n = MCsamp, min = min(x1.lims), max = max(x1.lims)),
                          x3 = x3.seq[i])
  res = predict(object = mod.dist, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res$mean - 2, sd = res$sd)
  Infer.x3.x2.x1 = rbind(Infer.x3.x2.x1, data.frame(x = x3.seq[i], prob = mean(fill.frame$p.del1), 
                                                    var = 'x3', cond = 'x2, x1'))
  # x1 | x2, x3
  x2.fill = c(runif(n = MCsamp.x2.x3.rng1, min = min(x2.lims.x3.rng1), max = max(x2.lims.x3.rng1)),
              runif(n = MCsamp.x2.x3.rng2, min = min(x2.lims.x3.rng2), max = max(x2.lims.x3.rng2)),
              runif(n = MCsamp.x2.x3.rng3, min = min(x2.lims.x3.rng3), max = max(x2.lims.x3.rng3)))
  fill.frame = data.frame(x2 = x2.fill, x3 = runif(n = MCsamp, min = min(x3.lims), max = max(x3.lims)),
                          x1 = x1.seq[i])
  res = predict(object = mod.dist, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res$mean - 2, sd = res$sd)
  Infer.x1.x2.x3 = rbind(Infer.x1.x2.x3, data.frame(x = x1.seq[i], prob = mean(fill.frame$p.del1), 
                                                    var = 'x1', cond = 'x2, x3'))
}

# Combine results for visualization
Infer.plt = rbind(Infer.x1, Infer.x2, Infer.x3, Infer.x2.x1, Infer.x2.x3, 
                  Infer.x1.x2.x3, Infer.x3.x2.x1);
write.csv(Infer.plt, 'Marginals_Accept_Delta1.csv')
rm(res, x2.fill, fill.frame)
```


```{r}
Infer.plt = read.csv(file = 'Marginals_Accept_Delta1.csv')

ggplot(filter(Infer.plt, cond == 'none')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(var))) +
  labs(x = expression('x'), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Variable') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()

ggplot(filter(Infer.plt, var == 'x2')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(cond))) +
  labs(x = expression('x'[2]), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Partial Conditions') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()

ggplot(filter(Infer.plt, cond == 'x2, x3' | cond == 'x2, x1' | cond == 'none', var != 'x2')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(cond))) +
  facet_wrap(~var, nrow = 2) +
  labs(x = 'x', y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Partial Conditions') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()


```
```{r}
rm(list = ls(pattern = "^Infer\\."))
```

While the peak probabilities after 2 conditionals are similar (around 80% probability at the best input value) regardless of order, it becomes more obvious the rationale for picking variables from most to least important when looking at $x_2 | x_1$ compared to $x_2 | x_3$. When the more important $x_3$ is known, the probability of acceptance is very high (> 75% at the peak), but when $x_1$ is known, the probability of acceptance for a specific $x_2$ value does not change from not knowing any additional information.

## Alternative Acceptance Criteria
For the purpose of illustration, the above method will be repeated with two other acceptance criteria:
* Objective function values below a specific threshold.
* Within a specific normalized distance of the utopia point and a specified prioritization of the two objective functions.

### Threshold cutoff
For simplicity, the cutoff values are the normalized values of 1 for both objectives. This is criteria, the acceptable points are those that fall within the normalized box defined by the utopia point (0,0) and the pseudo-nadir point (1,1).

Load the original dataset.

```{r Threshold: Load original data}
# Load data
GPar.all = read.csv(file = 'GPar_all_start.csv')
GPar.front = read.csv(file = 'GPar_fnt_start.csv')

# Remove leading indices: check if the first name is x1
while(names(GPar.all)[1] != 'x1'){
  GPar.all = GPar.all[,2:length(names(GPar.all))]
}
while(names(GPar.front)[1] != 'x1'){
  GPar.front = GPar.front[,2:length(names(GPar.front))]
}

```

```{r Treshold: First iteration, message=FALSE, warning=FALSE}
fill.sample.mod = function(GPar.data, input.name, output.name){
  # Calculate the GP model to use. 
  # Using the km function, but applies checks on the system to make sure that 
  # the model uncertainty matches expectations based on GP, ie. it did not
  # fail to converge.
  
  # Based on testing, the model is bad when the 10% percentile and 90% percentile 
  # of the standard deviation are of the same order of magnitude. This is easiest
  # checked if the difference between the 10th and 90th percentile
  # is larger than the difference between the 25th and 75th.
  pt10 = 1; pt90 = 1; pt25 = 1; pt75 = 1
  while(log10(pt90/pt10) <= log10(pt75/pt25)){
    mod.out = km(design = GPar.data[, input.name], response = GPar.data[, output.name], 
                 covtyp = 'gauss', # Gaussian uncertainty
                 optim.method = 'gen', # Genetic algorithm optimization
                 control = list(trace = FALSE, # Turn off tracking to simplify output
                                pop.size = 50), # Increase robustness
                 nugget = 1e-6, # Avoid eigenvalues of 0
                 )
    
    # Randomly sample 200 points from the search space
    pt = 200; i = 1
    lims = range(GPar.data[,input.name[i]])
    samp = data.frame(runif(n = pt, min = lims[1], max = lims[2]))
    for(i in 2:length(input.name)){
      lims = range(GPar.data[,input.name[i]])
      samp[,i] = runif(n = pt, min = lims[1], max = lims[2])
    }
    names(samp) = input.name
    
    # Find model output to find the percentile ranks for this iteration
    res = predict(object = mod.out, newdata = samp, type = 'UK')
    pt10 = quantile(res$sd, 0.10); pt90 = quantile(res$sd, 0.90)
    pt25 = quantile(res$sd, 0.25); pt75 = quantile(res$sd, 0.75)
  }
  return(mod.out)
}
fill.sample.obj2 = function(x, model.f1, model.f2){
  # Given data that contains: function evaluations (f1, f2) at inputs (x1, x2), 
  # and the normalized distance of (f1, f2) to the Pareto front
  # the function will output the objective function evaluated at x = (x1, x2)
  
  # Evaluate the Kriging model function at x 
  res.f1 = predict(object = model.f1, newdata = data.frame(x1 = x[1], x2 = x[2], x3 = x[3]), type = 'UK')
  res.f2 = predict(object = model.f2, newdata = data.frame(x1 = x[1], x2 = x[2], x3 = x[3]), type = 'UK')
  
  # Probability distribution fits a Gaussian distribution
  prob = pnorm(q = 0, mean = res.f1$mean - 2, sd = res.f1$sd) * 
    pnorm(q = 0, mean = res.f2$mean - 2, sd = res.f2$sd)
  
  # Variance based on propagation of errors, assuming independent measures
  # sd = (res.f1$sd^2*res.f2$mean^2 + res.f2$sd^2*res.f1$mean^2)
  sd = sqrt(res.f1$sd^2*res.f2$mean^2 + res.f2$sd^2*res.f1$mean^2)

  # Objective result
  return(sd*(prob*(1-prob) + 0.25/9))
}

# Search for the first point
mod.f1 = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'f1.norm')
mod.f2 = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'f2.norm')
GA.pred = ga(type = 'real-valued',
             fitness = function(x){fill.sample.obj2(x, model.f1 = mod.f1, model.f2 = mod.f2)},
             lower = c(0, 0, 0), upper = c(1, 1, 1),
             popSize = 100, maxiter = 100, run = 10, monitor = FALSE,
             parallel = 2)
# Next point to sample is the solution to this optimization
point.next = GA.pred@solution[1,]

# Account for the possibility that the genetic algorithm converges on multiple equivalent points
GPar.new = data.frame(x1 = point.next[1], x2 = point.next[2], x3 = point.next[3])
res = ZDT4.mod(x = as.matrix(GPar.new))
GPar.new$f1 = res[,1]; GPar.new$f2 = res[,2]
GPar.front = fill.sample.front.check(point.new = GPar.new, front.old = GPar.front)
# Fill in the remaining calculations: normalized outputs, distance, theta, order
GPar.new = n.obj(GPar.data = GPar.new, GPar.front = GPar.front)
cl <- makeCluster(2)
registerDoParallel(cl)
dist = foreach(row = 1:nrow(GPar.new)) %dopar%
  n.dist(f1.norm = GPar.new$f1.norm[row], f2.norm = GPar.new$f2.norm[row], GPar.front = GPar.front)
stopCluster(cl)
GPar.new$dist = unlist(dist)
GPar.new$theta = atan(GPar.new$f2.norm/GPar.new$f1.norm)*180/pi*10/9
GPar.new$order = max(GPar.all$order) + 1

# The cutoff point for the loop is 20 additional points or when the fitness value is less than half of this starting fitness value
start.fit = max(GA.pred@fitness)
# Store first point for plotting
GPar.new1 = GPar.new
rm(dist)

# Store the initial mod.dist for later
mod.f1.init = mod.f1
mod.f2.init = mod.f2
```

Visualize the first loop again to show that the set of the acceptable points is different due to the different criteria.

```{r Threshold: First Iteration}
lower = c(0, 0.3, 0); upper = c(1, 0.7, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x3 = c(GPar.new$x3),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x2 = c(seq(from = lower[3], to = upper[3], length.out = 50)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x3', 'x2')
# Apply Kriging function of distance
res = predict(object = mod.f1.init, newdata = fine.grid, type = "UK")
fine.grid$f1.mean = res$mean
fine.grid$f1.sd = res$sd

res = predict(object = mod.f2.init, newdata = data.frame(x1 = fine.grid$x1, 
                     x2 = fine.grid$x2, x3 = fine.grid$x3), type = "UK")
fine.grid$f2.mean = res$mean
fine.grid$f2.sd = res$sd

# Probability that the distance is less than 1
fine.grid$prob = pnorm(q = 0, mean = fine.grid$f1.mean - 2, sd = fine.grid$f1.sd) * 
  pnorm(q = 0, mean = fine.grid$f2.mean - 2, sd = fine.grid$f2.sd)
fine.grid$uncert = fine.grid$prob*(1-fine.grid$prob)+1e-10

# Information gain = variance = (var1*mean2)^2 + (var2*mean1)^2
fine.grid$info = (fine.grid$f1.sd/max(fine.grid$f1.sd))^2 + (fine.grid$f2.sd/max(fine.grid$f2.sd))^2

ncolor = 7
g1 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = uncert, z = uncert), 
                      breaks = seq(from = 0, to = 0.25, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = '', y = 'x2', title = 'Uncertainty')
rng = range(fine.grid$info)
g2 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = info, z = info), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = 'x1', y = '', title = 'Information Gain')
rng = range(fine.grid$info*fine.grid$uncert)
g3 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = uncert*info, z = uncert*info), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr",  name = '')  +
  labs(x = '', y = '', title = 'Sample Utility')
(g1 + guides(fill = FALSE)) + (g2 + guides(fill = FALSE)) + g3

## x3 slices
lower = c(0, 0.3, 0); upper = c(1, 0.7, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x2 = c(GPar.new$x2),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x3 = c(seq(from = lower[3], to = upper[3], length.out = 50)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x2', 'x3')
# Apply Kriging function of distance
res = predict(object = mod.f1.init, newdata = fine.grid, type = "UK")
fine.grid$f1.mean = res$mean
fine.grid$f1.sd = res$sd

res = predict(object = mod.f2.init, newdata = data.frame(x1 = fine.grid$x1, 
                     x2 = fine.grid$x2, x3 = fine.grid$x3), type = "UK")
fine.grid$f2.mean = res$mean
fine.grid$f2.sd = res$sd

# Probability that the distance is less than 1
fine.grid$prob = pnorm(q = 0, mean = fine.grid$f1.mean - 2, sd = fine.grid$f1.sd) * 
  pnorm(q = 0, mean = fine.grid$f2.mean - 2, sd = fine.grid$f2.sd)
fine.grid$uncert = fine.grid$prob*(1-fine.grid$prob)+1e-10

# Information gain = variance = (var1*mean2)^2 + (var2*mean1)^2
fine.grid$info = (fine.grid$f1.sd/max(fine.grid$f1.sd))^2 + (fine.grid$f2.sd/max(fine.grid$f2.sd))^2

g1 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = uncert, z = uncert), 
                      breaks = seq(from = 0, to = 0.25, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = '', y = 'x3', title = 'Uncertainty')
rng = range(fine.grid$info)
g2 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = info, z = info), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = 'x1', y = '', title = 'Information Gain')
rng = range(fine.grid$info*fine.grid$uncert)
g3 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = uncert*info, z = uncert*info), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr", name = '')  +
  labs(x = '', y = '', title = 'Sample Utility')

(g1 + guides(fill = FALSE)) + (g2 + guides(fill = FALSE)) + g3

rm(g1, g2, g3, fine.grid)
```


```{r Threshold: Iterations, message=FALSE, warning=FALSE}
budget = 20
next.fit = start.fit
while(next.fit > start.fit*0.005 & max(GPar.all$order) < budget+Pareto.budget){
  # Add the  new point to the dataset
  GPar.all = rbind(GPar.all, GPar.new)
  
  # Create a Kriging model for the distance
  mod.f1 = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'f1.norm')
  mod.f2 = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'f2.norm')
  GA.pred = ga(type = 'real-valued',
               fitness = function(x){fill.sample.obj2(x, model.f1 = mod.f1, model.f2 = mod.f2)},
               lower = c(0, 0, 0), upper = c(1, 1, 1),
               popSize = 100, maxiter = 100, run = 10, monitor = FALSE,
               parallel = 2)
  
  # Next point to sample is the solution to this optimization. 
  # Account for the possibility that the genetic algorithm converges on multiple equivalent points
  point.next = GA.pred@solution[1,]
  
  # Find values of the selected point
  GPar.new = data.frame(x1 = point.next[1], x2 = point.next[2], x3 = point.next[3])
  res = ZDT4.mod(x = as.matrix(GPar.new))
  GPar.new$f1 = res[,1]; GPar.new$f2 = res[,2]
  GPar.front = fill.sample.front.check(point.new = GPar.new, front.old = GPar.front)

  # Fill in the remaining caluclations: normalized outputs, distance, theta, order
  GPar.new = n.obj(GPar.data = GPar.new, GPar.front = GPar.front)
  cl <- makeCluster(2)
  registerDoParallel(cl)
  dist = foreach(row = 1:nrow(GPar.new)) %dopar%
    n.dist(f1.norm = GPar.new$f1.norm[row], f2.norm = GPar.new$f2.norm[row], GPar.front = GPar.front)
  stopCluster(cl)
  GPar.new$dist = unlist(dist)
  GPar.new$theta = atan(GPar.new$f2.norm/GPar.new$f1.norm)*180/pi*10/9
  GPar.new$order = max(GPar.all$order) + 1
  
  # The cutoff point for the loop is 20 additional points or when the fitness value is less than half of this starting fitness value
  next.fit = max(GA.pred@fitness)
}

GPar.all = rbind(GPar.all, GPar.new)
write.csv(GPar.all, 'GPar_Accept_Threshold.csv')

rm(res)
```

```{r Treshold: Visualize Iterations}
# Plot results on top of the most recent Kriging model
GPar.all = read.csv(file = 'GPar_Accept_Threshold.csv')
# Create a Kriging model for the distance
mod.f1 = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'f1.norm')
mod.f2 = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'f2.norm')

lower = c(0, 0.3, 0); upper = c(1, 0.7, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x3 = c(GPar.new$x3),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x2 = c(seq(from = lower[3], to = upper[3], length.out = 50)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x3', 'x2')
# Apply Kriging function of distance
res = predict(object = mod.f1, newdata = fine.grid, type = "UK")
fine.grid$f1.mean = res$mean
fine.grid$f1.sd = res$sd

res = predict(object = mod.f2, newdata = data.frame(x1 = fine.grid$x1, 
                     x2 = fine.grid$x2, x3 = fine.grid$x3), type = "UK")
fine.grid$f2.mean = res$mean
fine.grid$f2.sd = res$sd

# Probability that the distance is less than 1
fine.grid$prob = pnorm(q = 0, mean = fine.grid$f1.mean - 2, sd = fine.grid$f1.sd) * 
  pnorm(q = 0, mean = fine.grid$f2.mean - 2, sd = fine.grid$f2.sd)
fine.grid$uncert = fine.grid$prob*(1-fine.grid$prob)+1e-10

# Information gain = variance = (var1*mean2)^2 + (var2*mean1)^2
fine.grid$info = (fine.grid$f1.sd/max(fine.grid$f1.sd))^2 + (fine.grid$f2.sd/max(fine.grid$f2.sd))^2

ncolor = 7
g1 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = uncert, z = uncert), 
                      breaks = seq(from = 0, to = 0.25, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x2, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = '', y = 'x2', title = 'Uncertainty')
rng = range(fine.grid$info)
g2 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = info, z = info), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x2, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = 'x1', y = '', title = 'Information Gain')
rng = range(fine.grid$info*fine.grid$uncert)
g3 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x2, color = uncert*info, z = uncert*info), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x2, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x2), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr",  name = '')  +
  labs(x = '', y = '', title = 'Sample Utility')
(g1 + guides(fill = FALSE)) + (g2 + guides(fill = FALSE)) + g3

## x3 slices
lower = c(0, 0.3, 0); upper = c(1, 0.7, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x2 = c(GPar.new$x2),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x3 = c(seq(from = lower[3], to = upper[3], length.out = 50)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x2', 'x3')
# Apply Kriging function of distance
res = predict(object = mod.f1, newdata = fine.grid, type = "UK")
fine.grid$f1.mean = res$mean
fine.grid$f1.sd = res$sd

res = predict(object = mod.f2, newdata = data.frame(x1 = fine.grid$x1, 
                     x2 = fine.grid$x2, x3 = fine.grid$x3), type = "UK")
fine.grid$f2.mean = res$mean
fine.grid$f2.sd = res$sd

# Probability that the distance is less than 1
fine.grid$prob = pnorm(q = 0, mean = fine.grid$f1.mean - 2, sd = fine.grid$f1.sd) * 
  pnorm(q = 0, mean = fine.grid$f2.mean - 2, sd = fine.grid$f2.sd)
fine.grid$uncert = fine.grid$prob*(1-fine.grid$prob)+1e-10

# Information gain = variance = (var1*mean2)^2 + (var2*mean1)^2
fine.grid$info = (fine.grid$f1.sd/max(fine.grid$f1.sd))^2 + (fine.grid$f2.sd/max(fine.grid$f2.sd))^2

g1 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = uncert, z = uncert), 
                      breaks = seq(from = 0, to = 0.25, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x3, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = '', y = 'x3', title = 'Uncertainty')
rng = range(fine.grid$info)
g2 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = info, z = info), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x3, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  labs(x = 'x1', y = '', title = 'Information Gain')
rng = range(fine.grid$info*fine.grid$uncert)
g3 = ggplot(fine.grid) +
  geom_contour_filled(mapping = aes(x = x1, y = x3, color = uncert*info, z = uncert*info), 
                      breaks = seq(from = rng[1]*0.99, to = rng[2]*1.01, length.out = ncolor), alpha = 0.5) +
  geom_point(data = GPar.all, mapping = aes(x = x1, y = x3, color = order), size = 1.5, alpha = 0.5) +
  geom_point(data = GPar.new, mapping = aes(x = x1, y = x3), color = 'red', size = 3) +
  guides(color = FALSE) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr", name = '')  +
  labs(x = '', y = '', title = 'Sample Utility')

(g1 + guides(fill = FALSE)) + (g2 + guides(fill = FALSE)) + g3

rm(g1, g2, g3, fine.grid)
```

As indicated by this acceptance criteria, the boundary of the set it well defined with just the Pareto frontier, so additional iterations are not as necessary. Continuing with the procedure to show the feature importance and acceptance probability procedures.

```{r Threshold Feature Importance: Correlation Coefficient and Slope}
# Load data
GPar.all = read.csv(file = 'GPar_Accept_Threshold.csv')
GPar.front = read.csv(file = 'GPar_fnt_start.csv')
# Remove leading indices: the names are:
while(names(GPar.all)[1] != 'x1'){
  GPar.all = GPar.all[,2:length(names(GPar.all))]
}
while(names(GPar.front)[1] != 'x1'){
  GPar.front = GPar.front[,2:length(names(GPar.front))]
}

# Define the process used to collect the point
GPar.all$proc = 'Initial'
GPar.all$proc[GPar.all$order > 0] = 'Pareto'
GPar.all$proc[GPar.all$order > Pareto.budget] = 'Post'
# Break up the prioritization into favoring f1, f2, or a balance of the two
GPar.all$region = "f1"
GPar.all$region[GPar.all$theta < 200/3] = "50:50"
GPar.all$region[GPar.all$theta < 100/3] = "f2"

pt.size = 3
g1 = ggplot() +
  geom_point(data = filter(GPar.all, dist > 1), mapping = aes(x = theta, y = x1, shape = proc), color = 'red', size = pt.size) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x1), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x1, color = dist, shape = proc), size = pt.size) +
  labs(x = "", y = expression("x"[1]), color = "Distance:\nObjective\nSpace") +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(shape = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g2 = ggplot() +
  geom_point(data = filter(GPar.all, dist >  1), mapping = aes(x = theta, y = x2, shape = proc), color = 'red', size = pt.size) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x2), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x2, color = dist, shape = proc), size = pt.size) +
  labs(x = "Trade-Off", y = expression("x"[2]), color = "", shape = 'Collection\nProcess') +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(color = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g3 = ggplot() +
  geom_point(data = filter(GPar.all, dist >  1), mapping = aes(x = theta, y = x3, shape = proc), color = 'red', size = pt.size) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x3), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x3, color = dist, shape = proc), size = pt.size) +
  labs(x = "Trade-Off", y = expression("x"[3]), color = "", shape = 'Collection\nProcess') +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(color = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g1 / g2 / g3

# Approximate the Pareto front with a smoothed line using a Savitzky-Golay filter
Pfront.x1 = loess(x1 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                                x1 = filter(GPar.all, dist == 0)$x1))
Pfront.x2 = loess(x2 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                               x2 = filter(GPar.all, dist == 0)$x2))
Pfront.x3 = loess(x3 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                               x3 = filter(GPar.all, dist == 0)$x3))

# Store the information in a dataframe for visualization
plt = data.frame(theta = seq(from = 0, to = 100, length.out = 100))
res1 = predict(object = Pfront.x1, newdata = plt)
res2 = predict(object = Pfront.x2, newdata = plt)
res3 = predict(object = Pfront.x3, newdata = plt)
plt$x1 = unname(res1); plt$x2 = unname(res2); plt$x3 = unname(res3)
# Check the Savitzky–Golay filter smoothing quality
gx1 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x1)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x1))
gx2 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x2)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x2))
gx3 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x3)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x3))
gx1 / gx2 / gx3

# Apply the model to find the linear distance (regression)
GPar.all$x1.loess.Err = abs(GPar.all$x1 - predict(object = Pfront.x1, newdata = GPar.all$theta))
GPar.all$x2.loess.Err = abs(GPar.all$x2 - predict(object = Pfront.x2, newdata = GPar.all$theta))
GPar.all$x3.loess.Err = abs(GPar.all$x3 - predict(object = Pfront.x3, newdata = GPar.all$theta))

# Calculate the correlation coefficient of the log(objective distance) with the linear distance
x1.cor = cor(x = filter(GPar.all, dist > 0)$x1.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
x2.cor = cor(x = filter(GPar.all, dist > 0)$x2.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
x3.cor = cor(x = filter(GPar.all, dist > 0)$x3.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
# Calculate the slope of the linear relationship
x1.slp = lm((dist) ~ x1.loess.Err, data = filter(GPar.all, dist > 0))
x2.slp = lm((dist) ~ x2.loess.Err, data = filter(GPar.all, dist > 0))
x3.slp = lm((dist) ~ x3.loess.Err, data = filter(GPar.all, dist > 0))
x1.slp = unname(x1.slp$coefficients[2]); x2.slp = unname(x2.slp$coefficients[2])
x3.slp = unname(x3.slp$coefficients[2])

sz = 3
# Store information in a dataframe for plotting
GPar.cor.plt = data.frame(obj.dist = rep(GPar.all$dist, 3),
                          inp.dist = c(GPar.all$x1.loess.Err, GPar.all$x2.loess.Err, GPar.all$x3.loess.Err),
                          var = c(rep('x1', nrow(GPar.all)), rep('x2', nrow(GPar.all)), rep('x3', nrow(GPar.all))),
                          region = rep(GPar.all$region, 3),
                          val = c(GPar.all$x1, GPar.all$x2, GPar.all$x3))
var.labs <- c(paste('x1, r = ', round(x1.cor, 3), '; slope = ', round(x1.slp, 3)), 
              paste('x2, r = ', round(x2.cor, 3), '; slope = ', round(x2.slp, 3)),
              paste('x3, r = ', round(x3.cor, 3), '; slope = ', round(x3.slp, 3)))
names(var.labs) <- c("x1", "x2", "x3")

ggplot(GPar.cor.plt) +
  geom_point(mapping = aes(x = inp.dist, y = (obj.dist), shape = region, color = val), size = sz) +
  facet_grid(~var, labeller = labeller(var = var.labs)) + 
  labs(x = 'Distance: Input Space', y = expression('log'[10]*' Distance: Objective Space'), shape = 'Priority',
       color = 'Input Value')

rm(g1, g2, g3, gx1, gx2, gx3, Pfront.x1, Pfront.x2, Pfront.x3, plt, GPar.cor.plt)
```

As with the Pareto distance, $x_2$ and $x_3$ should have equal importance, but $x_3$ appears to be more important given the dataset bias.

```{r Threshold: Marginalization}
# Use the final GP model with the full dataset
mod.f1 = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'f1.norm')
mod.f2 = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'f2.norm')

# Obtain marginalized probabilities with a fine resolution grid (50 points). Calculate the integral with a Monte Carlo sampling of 500 samples each.
resolution = 50; MCsamp = 1500
x1.rng = range(GPar.all$x1); x2.rng = range(GPar.all$x2); x3.rng = range(GPar.all$x3)
x1.seq = seq(from = min(x1.rng), to = max(x1.rng), length.out = resolution)
x2.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)
x3.seq = seq(from = min(x3.rng), to = max(x3.rng), length.out = resolution)

Infer.x1 = data.frame(); Infer.x2 = data.frame(); Infer.x3 = data.frame()

for(i in 1:resolution){
  # x1
  fill.frame = data.frame(x1 = x1.seq[i], x2 = runif(n = MCsamp, min = min(x2.rng), max = max(x2.rng)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res1 = predict(object = mod.f1, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.f2, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * pnorm(q = 0, mean = res2$mean - 2, sd = res2$sd)
  Infer.x1 = rbind(Infer.x1, data.frame(x = x1.seq[i], prob = mean(fill.frame$p.del1), var = 'x1', cond = 'none'))
  
  # x2
  fill.frame = data.frame(x2 = x2.seq[i], x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res1 = predict(object = mod.f1, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.f2, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * pnorm(q = 0, mean = res2$mean - 2, sd = res2$sd)
  Infer.x2 = rbind(Infer.x2, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'none'))
  
  # x3
  fill.frame = data.frame(x3 = x3.seq[i], x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)),
                          x2 = runif(n = MCsamp, min = min(x2.rng), max = max(x2.rng)))
  res1 = predict(object = mod.f1, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.f2, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * pnorm(q = 0, mean = res2$mean - 2, sd = res2$sd)
  Infer.x3 = rbind(Infer.x3, data.frame(x = x3.seq[i], prob = mean(fill.frame$p.del1), var = 'x3', cond = 'none'))
}

ggplot() +
  geom_path(data = Infer.x1, mapping = aes(x = x, y = prob, color = var)) +
  geom_path(data = Infer.x2, mapping = aes(x = x, y = prob, color = var)) +
  geom_path(data = Infer.x3, mapping = aes(x = x, y = prob, color = var)) +
  labs(x = expression('x'), y = 'Probability of Acceptance', subtitle = expression('Accept if f'[1]*' < 1 & f'[2]*' < 1')) +
  scale_color_manual(name = 'Variable', values = c('x1' = 'red', 'x2' = 'blue', 'x3' = 'maroon'), 
                    labels = c('x1' = expression('x'[1]), 'x2' = expression('x'[2]),'x3' = expression('x'[3]))) +
  theme_bw()

```

Results for the importance rankings based on probability with this criteria is similar to the profiles for Pareto distance, although the peaks appear sharper.

```{r Threshold: Partial Conditional Probabilities}
# Determining the ranges
# Function to find the optimal range given the probability of acceptance
p.lims = function(data.prob, p.target){
  # data.prob is a dataframe with variables x and prob, which are the values and probability of acceptance
  
  # Limits are the range where the probability is at least half the maximim
  # p.target = 0.5*max(data.prob$prob)
  
  # Initial limits
  x.lims = range(filter(data.prob, prob >= p.target)$x)
  
  # Linear interpolate to find the proper point, assuming that the limit is not already the minimum possible value
  if(x.lims[1] > min(data.prob$x)){
    pos = which.min(abs(data.prob$x - x.lims[1]))
    sub = data.prob[c(pos-1, pos), ]
    mod = lm(x~prob, data = sub)
    res = predict(object = mod, newdata = data.frame(prob = p.target))
    x.lims[1] = res
  }
  if(x.lims[2] < max(data.prob$x)){
    pos = which.min(abs(data.prob$x - x.lims[2]))
    sub = data.prob[c(pos, pos+1), ]
    mod = lm(x ~ prob, data = sub)
    res = predict(object = mod, newdata = data.frame(prob = p.target))
    x.lims[2] = res
    rm(mod)
  }
  return(x.lims)
}
x1.lims = p.lims(data.prob = Infer.x1, p.target = 0.5*max(Infer.x1$prob))
x3.lims = p.lims(data.prob = Infer.x3, p.target = 0.5*max(Infer.x3$prob))

## Given that x1 or x3 is optimal, find the next variable in the series: x2
resolution = 50; MCsamp = 1500
x2.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)

# Single conditional: x2|x1 or x2|x3
Infer.x2.x1 = data.frame(); Infer.x2.x3 = data.frame()

for(i in 1:resolution){
  # x2 | x1
  fill.frame = data.frame(x2 = x2.seq[i], x1 = runif(n = MCsamp, min = min(x1.lims), max = max(x1.lims)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res1 = predict(object = mod.f1, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.f2, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * pnorm(q = 0, mean = res2$mean - 2, sd = res2$sd)
  Infer.x2.x1 = rbind(Infer.x2.x1, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'x1'))
  # x2 | x3
  fill.frame = data.frame(x2 = x2.seq[i], x3 = runif(n = MCsamp, min = min(x3.lims), max = max(x3.lims)),
                          x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)))
  res1 = predict(object = mod.f1, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.f2, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * pnorm(q = 0, mean = res2$mean - 2, sd = res2$sd)
  Infer.x2.x3 = rbind(Infer.x2.x3, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'x3'))
}

ggplot(rbind(Infer.x2.x3, Infer.x2.x1)) +
  geom_path(mapping = aes(x = x, y = prob, color = cond)) +
  labs(x = expression('x'[2]), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'),
       color = 'Given optimal') +
  theme_bw()

# Instead of a simple range, the multimodal peaks of these probability curves mean a simple min/max bound can be used. While a nearest-neighbor approximation would work, a faster solution is to find 3 separate ranges.
x2.lims.x3.rng1 = p.lims(data.prob = filter(Infer.x2.x3, x < 0.25), 
                         p.target = max(Infer.x2.x3$prob)*0.5)
x2.lims.x3.rng2 = p.lims(data.prob = filter(Infer.x2.x3, x > 0.25, x < 0.75), 
                         p.target = max(Infer.x2.x3$prob)*0.5)
x2.lims.x3.rng3 = p.lims(data.prob = filter(Infer.x2.x3, x > 0.75), 
                         p.target = max(Infer.x2.x3$prob)*0.5)
x2.lims.x1.rng1 = p.lims(data.prob = filter(Infer.x2.x1, x < 0.25), 
                         p.target = max(Infer.x2.x1$prob)*0.5)
x2.lims.x1.rng2 = p.lims(data.prob = filter(Infer.x2.x1, x > 0.25, x < 0.75), 
                         p.target = max(Infer.x2.x1$prob)*0.5)
x2.lims.x1.rng3 = p.lims(data.prob = filter(Infer.x2.x1, x > 0.75), 
                         p.target = max(Infer.x2.x1$prob)*0.5)
# The number of points to collect from each range is proportional to their relative widths

## Given that x1 or x3 is optimal, find the next variable in the series: x2
# resolution = 50; MCsamp = 1500
MCsamp.x2.x3.rng1 = round(1500*diff(x2.lims.x3.rng1)/
                            (diff(x2.lims.x3.rng1) + diff(x2.lims.x3.rng2) + diff(x2.lims.x3.rng3)))
MCsamp.x2.x3.rng2 = round(1500*diff(x2.lims.x3.rng2)/
                            (diff(x2.lims.x3.rng1) + diff(x2.lims.x3.rng2) + diff(x2.lims.x3.rng3)))
MCsamp.x2.x3.rng3 = 1500 - MCsamp.x2.x3.rng1 - MCsamp.x2.x3.rng2
MCsamp.x2.x1.rng1 = round(1500*diff(x2.lims.x1.rng1)/
                            (diff(x2.lims.x1.rng1) + diff(x2.lims.x1.rng2) + diff(x2.lims.x1.rng3)))
MCsamp.x2.x1.rng2 = round(1500*diff(x2.lims.x1.rng2)/
                            (diff(x2.lims.x1.rng1) + diff(x2.lims.x1.rng2) + diff(x2.lims.x1.rng3)))
MCsamp.x2.x1.rng3 = 1500 - MCsamp.x2.x1.rng1 - MCsamp.x2.x1.rng2

x1.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)
x3.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)

# Single conditional: x2|x1 or x2|x3
Infer.x3.x2.x1 = data.frame(); Infer.x1.x2.x3 = data.frame()
for(i in 1:resolution){
  # x3 | x2, x1
  x2.fill = c(runif(n = MCsamp.x2.x1.rng1, min = min(x2.lims.x1.rng1), max = max(x2.lims.x1.rng1)),
              runif(n = MCsamp.x2.x1.rng2, min = min(x2.lims.x1.rng2), max = max(x2.lims.x1.rng2)),
              runif(n = MCsamp.x2.x1.rng3, min = min(x2.lims.x1.rng3), max = max(x2.lims.x1.rng3)))
  fill.frame = data.frame(x2 = x2.fill, x1 = runif(n = MCsamp, min = min(x1.lims), max = max(x1.lims)),
                          x3 = x3.seq[i])
  res1 = predict(object = mod.f1, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.f2, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * pnorm(q = 0, mean = res2$mean - 2, sd = res2$sd)
  Infer.x3.x2.x1 = rbind(Infer.x3.x2.x1, data.frame(x = x3.seq[i], prob = mean(fill.frame$p.del1), 
                                                    var = 'x3', cond = 'x2, x1'))
  # x1 | x2, x3
  x2.fill = c(runif(n = MCsamp.x2.x3.rng1, min = min(x2.lims.x3.rng1), max = max(x2.lims.x3.rng1)),
              runif(n = MCsamp.x2.x3.rng2, min = min(x2.lims.x3.rng2), max = max(x2.lims.x3.rng2)),
              runif(n = MCsamp.x2.x3.rng3, min = min(x2.lims.x3.rng3), max = max(x2.lims.x3.rng3)))
  fill.frame = data.frame(x2 = x2.fill, x3 = runif(n = MCsamp, min = min(x3.lims), max = max(x3.lims)),
                          x1 = x1.seq[i])
  res1 = predict(object = mod.f1, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.f2, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * pnorm(q = 0, mean = res2$mean - 2, sd = res2$sd)
  Infer.x1.x2.x3 = rbind(Infer.x1.x2.x3, data.frame(x = x1.seq[i], prob = mean(fill.frame$p.del1), 
                                                    var = 'x1', cond = 'x2, x3'))
}

# Combine results for visualization
Infer.plt = rbind(Infer.x1, Infer.x2, Infer.x3, Infer.x2.x1, Infer.x2.x3, 
                  Infer.x1.x2.x3, Infer.x3.x2.x1);
write.csv(Infer.plt, 'Marginals_Accept_Threshold.csv')
rm(res1, res2, x2.fill, fill.frame)
```

```{r}
Infer.plt = read.csv(file = 'Marginals_Accept_Threshold.csv')

ggplot(filter(Infer.plt, cond == 'none')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(var))) +
  labs(x = expression('x'), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Variable') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()

ggplot(filter(Infer.plt, cond == 'x2, x3' | cond == 'x2, x1' | cond == 'none', var != 'x2')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(cond))) +
  facet_wrap(~var, nrow = 2) +
  labs(x = 'x', y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Partial Conditions') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()

ggplot(filter(Infer.plt, var == 'x2')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(cond))) +
  labs(x = expression('x'[2]), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Partial Conditions') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()

```

```{r}
rm(list = ls(pattern = "^Infer\\."))

```

### Utopia Distance and Prioritization
Since the utopia point is set to (0,0), the distance to the utopia point is simple to calculate from the normalized coordinates. Acceptable points are those that prioritize the first objective by at least 80%, which can be determined by the angle theta.

Load the original dataset.

```{r Utopia Distance: Load Data}
# Load data
GPar.all = read.csv(file = 'GPar_all_start.csv')
GPar.front = read.csv(file = 'GPar_fnt_start.csv')

# Remove leading indices: the names are:
while(names(GPar.all)[1] != 'x1'){
  GPar.all = GPar.all[,2:length(names(GPar.all))]
}
while(names(GPar.front)[1] != 'x1'){
  GPar.front = GPar.front[,2:length(names(GPar.front))]
}
```

```{r Utopia Distance: First Iteration, message=FALSE, warning=FALSE}
fill.sample.mod = function(GPar.data, input.name, output.name){
  # Calculate the GP model to use. 
  # Using the km function, but applies checks on the system to make sure that 
  # the model uncertainty matches expectations based on GP, ie. it did not
  # fail to converge.
  
  # Based on testing, the model is bad when the 10% percentile and 90% percentile 
  # of the standard deviation are of the same order of magnitude. This is easiest
  # checked if the difference between the 10th and 90th percentile
  # is larger than the difference between the 25th and 75th.
  pt10 = 1; pt90 = 1; pt25 = 1; pt75 = 1
  while(log10(pt90/pt10) <= log10(pt75/pt25)){
    mod.out = km(design = GPar.data[, input.name], response = GPar.data[, output.name], 
                 covtyp = 'gauss', # Gaussian uncertainty
                 optim.method = 'gen', # Genetic algorithm optimization
                 control = list(trace = FALSE, # Turn off tracking to simplify output
                                pop.size = 50), # Increase robustness
                 nugget = 1e-6, # Avoid eigenvalues of 0
                 )
    
    # Randomly sample 200 points from the search space
    pt = 200; i = 1
    lims = range(GPar.data[,input.name[i]])
    samp = data.frame(runif(n = pt, min = lims[1], max = lims[2]))
    for(i in 2:length(input.name)){
      lims = range(GPar.data[,input.name[i]])
      samp[,i] = runif(n = pt, min = lims[1], max = lims[2])
    }
    names(samp) = input.name
    
    # Find model output to find the percentile ranks for this iteration
    res = predict(object = mod.out, newdata = samp, type = 'UK')
    pt10 = quantile(res$sd, 0.10); pt90 = quantile(res$sd, 0.90)
    pt25 = quantile(res$sd, 0.25); pt75 = quantile(res$sd, 0.75)
  }
  return(mod.out)
}
fill.sample.obj3 = function(x, model.f1, model.f2){
  # Given data that contains: function evaluations (f1, f2) at inputs (x1, x2), 
  # and the normalized distance of (f1, f2) to the Pareto front
  # the function will output the objective function evaluated at x = (x1, x2)
  
  # Evaluate the Kriging model function at x. In this case, f1 and f2 are models for utopia distance and angle.
  res.f1 = predict(object = model.f1, newdata = data.frame(x1 = x[1], x2 = x[2], x3 = x[3]), type = 'UK')
  res.f2 = predict(object = model.f2, newdata = data.frame(x1 = x[1], x2 = x[2], x3 = x[3]), type = 'UK')
  
  # Probability distribution fits a Gaussian distribution
  prob = pnorm(q = 0, mean = res.f1$mean - 2, sd = res.f1$sd) * 
    (1 - pnorm(q = 0, mean = res.f2$mean - 20, sd = res.f2$sd))
  
  # Variance based on propagation of errors
  sd = sqrt(res.f1$sd^2*res.f2$mean^2 + res.f2$sd^2*res.f1$mean^2)

  # Objective result
  return(sd*(prob*(1-prob) + 0.25/9))
}

# Search for the first point
GPar.all$rad = sqrt(GPar.all$f1.norm^2 + GPar.all$f2.norm^2)
mod.rad = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'rad')
mod.ang = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'theta')
GA.pred = ga(type = 'real-valued',
             fitness = function(x){fill.sample.obj3(x, model.f1 = mod.rad, model.f2 = mod.ang)},
             lower = c(0, 0, 0), upper = c(1, 1, 1),
             popSize = 100, maxiter = 100, run = 10, monitor = FALSE,
             parallel = 2)
# Next point to sample is the solution to this optimization
point.next = GA.pred@solution[1,]

# Account for the possibility that the genetic algorithm converges on multiple equivalent points
GPar.new = data.frame(x1 = point.next[1], x2 = point.next[2], x3 = point.next[3])
res = ZDT4.mod(x = as.matrix(GPar.new))
GPar.new$f1 = res[,1]; GPar.new$f2 = res[,2]
GPar.front = fill.sample.front.check(point.new = GPar.new, front.old = GPar.front)
# Fill in the remaining caluclations: normalized outputs, distance, theta, order
GPar.new = n.obj(GPar.data = GPar.new, GPar.front = GPar.front)
cl <- makeCluster(2)
registerDoParallel(cl)
dist = foreach(row = 1:nrow(GPar.new)) %dopar%
  n.dist(f1.norm = GPar.new$f1.norm[row], f2.norm = GPar.new$f2.norm[row], GPar.front = GPar.front)
stopCluster(cl)
GPar.new$dist = unlist(dist)
GPar.new$theta = atan(GPar.new$f2.norm/GPar.new$f1.norm)*180/pi*10/9
GPar.new$order = max(GPar.all$order) + 1
GPar.new$rad = sqrt(GPar.new$f1.norm^2 + GPar.new$f2.norm^2)

# The cutoff point for the loop is 20 additional points or when the fitness value is less than half of this starting fitness value
start.fit = max(GA.pred@fitness)
# Store first point for plotting
GPar.new1 = GPar.new
rm(dist)

# Store the initial mod.dist for later
mod.rad.init = mod.rad
mod.ang.init = mod.ang

# Grid of the relevant region to visualize
lower = c(0, 0, 0); upper = c(1, 1, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x2 = c(GPar.new$x2, seq(from = lower[2], to = upper[2], length.out = 25)),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x3 = c(GPar.new$x3, seq(from = lower[3], to = upper[3], length.out = 25)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x2', 'x3')

# Apply Kriging functions
res = predict(object = mod.rad.init, newdata = fine.grid, type = "UK")
fine.grid$rad.mean = res$mean
fine.grid$rad.sd = res$sd

res = predict(object = mod.ang.init, newdata = data.frame(x1 = fine.grid$x1, 
                      x2 = fine.grid$x2, x3 = fine.grid$x3), type = "UK")
fine.grid$ang.mean = res$mean
fine.grid$ang.sd = res$sd

# Uncertainty = P(success)*(1 - P(success))
fine.grid$prob = pnorm(q = 0, mean = fine.grid$rad.mean - 2, sd = fine.grid$rad.sd) * 
  (1 - pnorm(q = 0, mean = fine.grid$ang.mean - 20, sd = fine.grid$ang.sd))

# Information gain = variance = (var1*mean2)^2 + (var2*mean1)^2
fine.grid$info = (fine.grid$rad.sd/max(fine.grid$rad.sd))^2 + (fine.grid$ang.sd/max(fine.grid$ang.sd))^2

ncolor = 7; pt.size = 2.5
g1 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x3 == GPar.new$x3, x2 != GPar.new$x2), 
                      mapping = aes(x = x1, y = x2, z = (prob)*(1-prob)-1e-10,
                                    color = (prob)*(1-prob)-1e-10), alpha = 0.5,
                      breaks = seq(from = -0.01, to = 0.25, length.out = ncolor)
                      )+
  geom_contour(data = filter(fine.grid, x3 == GPar.new$x3, x2 != GPar.new$x2), 
               mapping = aes(x = x1, y = x2, z = prob), breaks = c(0.25, 0.75), color = 'blue') +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x2, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x2, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = GPar.new1, mapping = aes(x = x1, y = x2, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(palette = "PuOr") +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  labs(x = "", y = expression("x"[2]), subtitle = 'Uncertainty') +  guides(fill = FALSE, color = FALSE, shape = FALSE)

g2 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x3 == GPar.new$x3, x2 != GPar.new$x2), 
                      mapping = aes(x = x1, y = x2, z = info, color = info), bins = ncolor, alpha = 0.5)+
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x2, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x2, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = GPar.new1, mapping = aes(x = x1, y = x2, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(palette = "PuOr") +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  labs(x = expression("x"[1]), y = "", subtitle = 'Information Gain') +  guides(fill = FALSE, color = FALSE, shape = FALSE)

g3 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x3 == GPar.new$x3, x2 != GPar.new$x2), 
                      mapping = aes(x = x1, y = x2, z = info*(prob)*(1-prob), color = info*(prob)*(1-info)),
                      bins = ncolor, alpha = 0.5)+
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x2, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x2, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = GPar.new1, mapping = aes(x = x1, y = x2, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  labs(x = "", y = "", subtitle = "Sample Utility", fill = "", shape = 'Collection\nProcess', color = 'Collection\nProcess') +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  guides(color=guide_legend(override.aes=list(fill=NA))) # Remove fill in the legend

g1 + g2 + g3

g1 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x2 == GPar.new$x2, x3 != GPar.new$x3), 
                      mapping = aes(x = x1, y = x3, z = (prob)*(1-prob)-1e-10,
                                    color = (prob)*(1-prob)-1e-10), alpha = 0.5,
                      breaks = seq(from = -0.01, to = 0.25, length.out = ncolor)
                      )+
  geom_contour(data = filter(fine.grid, x2 == GPar.new$x2, x3 != GPar.new$x3),
               mapping = aes(x = x1, y = x3, z = prob), breaks = c(0.25, 0.75), color = 'blue') +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x3, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x3, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = GPar.new1, mapping = aes(x = x1, y = x3, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(palette = "PuOr") +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  labs(x = "", y = expression("x"[3]), subtitle = 'Uncertainty') +  guides(fill = FALSE, color = FALSE, shape = FALSE)

g2 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x2 == GPar.new$x2, x3 != GPar.new$x3), 
                      mapping = aes(x = x1, y = x3, z = info, color = info), bins = ncolor, alpha = 0.5)+
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x3, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x3, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = GPar.new1, mapping = aes(x = x1, y = x3, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(palette = "PuOr") +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  labs(x = expression("x"[1]), y = "", subtitle = 'Information Gain') +  guides(fill = FALSE, color = FALSE, shape = FALSE)

g3 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x2 == GPar.new$x2, x3 != GPar.new$x3), 
                      mapping = aes(x = x1, y = x3, z = info*(prob)*(1-prob), color = info*(prob)*(1-prob)),
                      bins = ncolor, alpha = 0.5)+
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x3, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x3, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = GPar.new1, mapping = aes(x = x1, y = x3, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  labs(x = "", y = "", subtitle = "Sample Utility", fill = "", 
       shape = 'Collection\nProcess', color = 'Collection\nProcess') +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  guides(color=guide_legend(override.aes=list(fill=NA))) # Remove fill in the legend

g1 + g2 + g3

# Sometimes the grid scan finds a point that is slightly better than the perceived optimum due to the convergence criteria. In that event, replace the starting point for the cutoff criteria for iteration
start.fit = max(start.fit, max(fine.grid$inf*fine.grid$prob*(1-fine.grid$prob)))

rm(g1, g2, g3, fine.grid)
```

```{r Utopia Distance: Repeated Iterations, message=FALSE, warning=FALSE}
budget = 20
next.fit = start.fit
while(next.fit > start.fit*0.005 & max(GPar.all$order) < budget+Pareto.budget){
  # Add the  new point to the dataset
  GPar.all = rbind(GPar.all, GPar.new)
  
  # Create a Kriging model for the distance
  mod.rad = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'rad')
  mod.ang = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'theta')
  GA.pred = ga(type = 'real-valued',
               fitness = function(x){fill.sample.obj3(x, model.f1 = mod.rad, model.f2 = mod.ang)},
               lower = c(0, 0, 0), upper = c(1, 1, 1),
               popSize = 100, maxiter = 100, run = 10, monitor = FALSE,
               parallel = 2)
  
  # Next point to sample is the solution to this optimization. 
  # Account for the possibility that the genetic algorithm converges on multiple equivalent points
  point.next = GA.pred@solution[1,]
  
  # Find values of the selected point
  GPar.new = data.frame(x1 = point.next[1], x2 = point.next[2], x3 = point.next[3])
  res = ZDT4.mod(x = as.matrix(GPar.new))
  GPar.new$f1 = res[,1]; GPar.new$f2 = res[,2]
  GPar.front = fill.sample.front.check(point.new = GPar.new, front.old = GPar.front)
  
  # Fill in the remaining caluclations: normalized outputs, distance, theta, order
  GPar.new = n.obj(GPar.data = GPar.new, GPar.front = GPar.front)
  cl <- makeCluster(2)
  registerDoParallel(cl)
  dist = foreach(row = 1:nrow(GPar.new)) %dopar%
    n.dist(f1.norm = GPar.new$f1.norm[row], f2.norm = GPar.new$f2.norm[row], GPar.front = GPar.front)
  stopCluster(cl)
  GPar.new$dist = unlist(dist)
  GPar.new$theta = atan(GPar.new$f2.norm/GPar.new$f1.norm)*180/pi*10/9
  GPar.new$order = max(GPar.all$order) + 1
  GPar.new$rad = sqrt(GPar.new$f1.norm^2 + GPar.new$f2.norm^2)
  
  # The cutoff point for the loop is 20 additional points or when the fitness value is less than half of this starting fitness value
  next.fit = max(GA.pred@fitness)
}

GPar.all = rbind(GPar.all, GPar.new)

write.csv(GPar.all, 'GPar_Accept_Radius.csv')

rm(res, cl, point.next)
```

```{r}
GPar.all = read.csv(file = 'GPar_Accept_Radius.csv')
# Plot results on top of the most recent Kriging model
mod.rad = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'rad')
mod.ang = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'theta')

# Grid of the relevant region to visualize
lower = c(0, 0, 0); upper = c(1, 1, 1)
fine.grid = expand.grid(x1 = seq(from = lower[1], to = upper[1], length.out = 50), 
                        x2 = c(GPar.new$x2, seq(from = lower[2], to = upper[2], length.out = 25)),
                        # x3 = c(0, 0.01, 0.1, 0.5, 1))
                        x3 = c(GPar.new$x3, seq(from = lower[3], to = upper[3], length.out = 25)))
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x2', 'x3')

# Apply Kriging functions
res = predict(object = mod.rad, newdata = fine.grid, type = "UK")
fine.grid$rad.mean = res$mean
fine.grid$rad.sd = res$sd

res = predict(object = mod.ang, newdata = data.frame(x1 = fine.grid$x1, 
                      x2 = fine.grid$x2, x3 = fine.grid$x3), type = "UK")
fine.grid$ang.mean = res$mean
fine.grid$ang.sd = res$sd

# Uncertainty = P(success)*(1 - P(success))
fine.grid$prob = pnorm(q = 0, mean = fine.grid$rad.mean - 2, sd = fine.grid$rad.sd) * 
  (1 - pnorm(q = 0, mean = fine.grid$ang.mean - 20, sd = fine.grid$ang.sd))

# Information gain = variance = (var1*mean2)^2 + (var2*mean1)^2
fine.grid$info = (fine.grid$rad.sd/max(fine.grid$rad.sd))^2 + (fine.grid$ang.sd/max(fine.grid$ang.sd))^2

ncolor = 7; pt.size = 2.5
g1 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x3 == GPar.new$x3, x2 != GPar.new$x2), 
                      mapping = aes(x = x1, y = x2, z = (prob)*(1-prob)-1e-10,
                                    color = (prob)*(1-prob)-1e-10), alpha = 0.5,
                      breaks = seq(from = -0.01, to = 0.25, length.out = ncolor)
                      )+
  geom_contour(data = filter(fine.grid, x3 == GPar.new$x3, x2 != GPar.new$x2), 
               mapping = aes(x = x1, y = x2, z = prob), breaks = c(0.25, 0.75), color = 'blue') +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x2, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x2, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = filter(GPar.all, order > Pareto.budget), 
             mapping = aes(x = x1, y = x2, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(palette = "PuOr") +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  labs(x = "", y = expression("x"[2]), subtitle = 'Uncertainty') +  guides(fill = FALSE, color = FALSE, shape = FALSE)

g2 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x3 == GPar.new$x3, x2 != GPar.new$x2), 
                      mapping = aes(x = x1, y = x2, z = info, color = info), bins = ncolor, alpha = 0.5)+
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x2, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x2, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = filter(GPar.all, order > Pareto.budget), 
             mapping = aes(x = x1, y = x2, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(palette = "PuOr") +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  labs(x = expression("x"[1]), y = "", subtitle = 'Information Gain') +  guides(fill = FALSE, color = FALSE, shape = FALSE)

g3 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x3 == GPar.new$x3, x2 != GPar.new$x2), 
                      mapping = aes(x = x1, y = x2, z = info*(prob)*(1-prob), color = info*(prob)*(1-info)),
                      bins = ncolor, alpha = 0.5)+
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x2, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x2, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = filter(GPar.all, order > Pareto.budget), 
             mapping = aes(x = x1, y = x2, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  labs(x = "", y = "", subtitle = "Sample Utility", fill = "", shape = 'Collection\nProcess', color = 'Collection\nProcess') +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  guides(color=guide_legend(override.aes=list(fill=NA))) # Remove fill in the legend

g1 + g2 + g3

g1 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x2 == GPar.new$x2, x3 != GPar.new$x3), 
                      mapping = aes(x = x1, y = x3, z = (prob)*(1-prob)-1e-10,
                                    color = (prob)*(1-prob)-1e-10), alpha = 0.5,
                      breaks = seq(from = -0.01, to = 0.25, length.out = ncolor)
                      )+
  geom_contour(data = filter(fine.grid, x2 == GPar.new$x2, x3 != GPar.new$x3),
               mapping = aes(x = x1, y = x3, z = prob), breaks = c(0.25, 0.75), color = 'blue') +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x3, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x3, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = filter(GPar.all, order > Pareto.budget), 
             mapping = aes(x = x1, y = x3, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(palette = "PuOr") +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  labs(x = "", y = expression("x"[3]), subtitle = 'Uncertainty') +  guides(fill = FALSE, color = FALSE, shape = FALSE)

g2 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x2 == GPar.new$x2, x3 != GPar.new$x3), 
                      mapping = aes(x = x1, y = x3, z = info, color = info), bins = ncolor, alpha = 0.5)+
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x3, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x3, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = filter(GPar.all, order > Pareto.budget), 
             mapping = aes(x = x1, y = x3, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(palette = "PuOr") +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  labs(x = expression("x"[1]), y = "", subtitle = 'Information Gain') +  guides(fill = FALSE, color = FALSE, shape = FALSE)

g3 = ggplot() +
  geom_contour_filled(data = filter(fine.grid, x2 == GPar.new$x2, x3 != GPar.new$x3), 
                      mapping = aes(x = x1, y = x3, z = info*(prob)*(1-prob), color = info*(prob)*(1-prob)),
                      bins = ncolor, alpha = 0.5)+
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], order == 0),
             mapping = aes(x = x1, y = x3, color = 'initial', shape = 'initial'), size = pt.size) +
  geom_point(data = filter(GPar.all, x1 <= upper[1], x1 >= lower[1], x2 <= upper[2], x2 >= lower[2], 
                           order > 0, order < Pareto.budget+1),
             mapping = aes(x = x1, y = x3, color = 'Pareto', shape = 'Pareto'), size = pt.size) +
  geom_point(data = filter(GPar.all, order > Pareto.budget), 
             mapping = aes(x = x1, y = x3, color = 'Post', shape = 'Post'), size = pt.size) +
  scale_fill_brewer(labels = c("Low", rep("", ncolor-3), "High"), palette = "PuOr")  +
  scale_color_manual(values = c('initial' = 'black', 'Pareto' = 'darkorchid3', 'Post' = 'red3'),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  scale_shape_manual(values = c('initial' = 15, 'Pareto' = 16, 'Post' = 17),
                     labels = c('Initial', 'Pareto', 'Post'), breaks = c('initial', 'Pareto', 'Post')) +
  labs(x = "", y = "", subtitle = "Sample Utility", fill = "", 
       shape = 'Collection\nProcess', color = 'Collection\nProcess') +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  guides(color=guide_legend(override.aes=list(fill=NA))) # Remove fill in the legend

g1 + g2 + g3

# x3 slices
sz.fine = 100
x1.rng = seq(from = 0, to = 1, length.out = sz.fine)
x2.rng = seq(from = 0, to = 1, length.out = sz.fine)
x3.rng = seq(from = 0, to = 1, length.out = 9) # Simple slice for visualization
fine.grid = expand.grid(x1.rng, x2.rng, x3.rng)
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x2', 'x3')

# Calculate
res = predict(object = mod.rad, newdata = fine.grid, type = "UK")
fine.grid$rad.mean = res$mean
fine.grid$rad.sd = res$sd
res = predict(object = mod.ang, newdata = data.frame(x1 = fine.grid$x1, 
                      x2 = fine.grid$x2, x3 = fine.grid$x3), type = "UK")
fine.grid$ang.mean = res$mean
fine.grid$ang.sd = res$sd
# Uncertainty = P(success)*(1 - P(success))
fine.grid$prob = pnorm(q = 0, mean = fine.grid$rad.mean - 2, sd = fine.grid$rad.sd) * 
  (1 - pnorm(q = 0, mean = fine.grid$ang.mean - 20, sd = fine.grid$ang.sd))

ggplot() +
  geom_point(data = fine.grid, mapping = aes(x = x1, y = x2, color = prob)) +
  labs(x = expression('x'[1]), y = expression('x'[2]), color = expression('P[accept]')) +
  theme_classic() + facet_wrap(~x3) + 
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))

# x2 slices
sz.fine = 100
x1.rng = seq(from = 0, to = 1, length.out = sz.fine)
x3.rng = seq(from = 0, to = 1, length.out = sz.fine)
x2.rng = seq(from = 0, to = 1, length.out = 9) # Simple slice for visualization
fine.grid = expand.grid(x1.rng, x2.rng, x3.rng)
fine.grid = fine.grid[,1:3]
names(fine.grid) = c('x1', 'x2', 'x3')

# Calculate
res = predict(object = mod.rad, newdata = fine.grid, type = "UK")
fine.grid$rad.mean = res$mean
fine.grid$rad.sd = res$sd
res = predict(object = mod.ang, newdata = data.frame(x1 = fine.grid$x1, 
                      x2 = fine.grid$x2, x3 = fine.grid$x3), type = "UK")
fine.grid$ang.mean = res$mean
fine.grid$ang.sd = res$sd
# Uncertainty = P(success)*(1 - P(success))
fine.grid$prob = pnorm(q = 0, mean = fine.grid$rad.mean - 2, sd = fine.grid$rad.sd) * 
  (1 - pnorm(q = 0, mean = fine.grid$ang.mean - 20, sd = fine.grid$ang.sd))

ggplot() +
  geom_point(data = fine.grid, mapping = aes(x = x1, y = x3, color = prob)) +
  labs(x = expression('x'[1]), y = expression('x'[3]), color = expression('P[accept]')) +
  theme_classic() + facet_wrap(~x2) + 
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))

rm(g1, g2, g3, fine.grid, res)
```


```{r Utopia distance Feature Importance: Correlation Coefficient and Slope}
# Load data
GPar.all = read.csv(file = 'GPar_Accept_Radius.csv')
GPar.front = read.csv(file = 'GPar_fnt_start.csv')
# Remove leading indices: the names are:
while(names(GPar.all)[1] != 'x1'){
  GPar.all = GPar.all[,2:length(names(GPar.all))]
}
while(names(GPar.front)[1] != 'x1'){
  GPar.front = GPar.front[,2:length(names(GPar.front))]
}

# Define the process used to collect the point
GPar.all$proc = 'Initial'
GPar.all$proc[GPar.all$order > 0] = 'Pareto'
GPar.all$proc[GPar.all$order > Pareto.budget] = 'Post'
# Break up the prioritization into favoring f1, f2, or a balance of the two
GPar.all$region = "f1"
GPar.all$region[GPar.all$theta < 200/3] = "50:50"
GPar.all$region[GPar.all$theta < 100/3] = "f2"

pt.size = 3
g1 = ggplot() +
  geom_point(data = filter(GPar.all, dist > 1), mapping = aes(x = theta, y = x1, shape = proc), color = 'red', size = pt.size) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x1), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x1, color = dist, shape = proc), size = pt.size) +
  labs(x = "", y = expression("x"[1]), color = "Distance:\nObjective\nSpace") +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(shape = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g2 = ggplot() +
  geom_point(data = filter(GPar.all, dist >  1), mapping = aes(x = theta, y = x2, shape = proc), color = 'red', size = pt.size) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x2), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x2, color = dist, shape = proc), size = pt.size) +
  labs(x = "Trade-Off", y = expression("x"[2]), color = "", shape = 'Collection\nProcess') +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(color = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g3 = ggplot() +
  geom_point(data = filter(GPar.all, dist >  1), mapping = aes(x = theta, y = x3, shape = proc), color = 'red', size = pt.size) +
  geom_smooth(data = filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x3), color = "black", level = 0) +
  geom_point(data = filter(GPar.all, dist <= 1), mapping = aes(x = theta, y = x3, color = dist, shape = proc), size = pt.size) +
  labs(x = "Trade-Off", y = expression("x"[3]), color = "", shape = 'Collection\nProcess') +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100), labels = c(expression("f"[2]*" min"), "", "50:50", "", expression("f"[1]*" min")), 
                     expand = c(0.01, 0.01)) +
  guides(color = FALSE) + theme_bw() + scale_y_continuous(expand = c(0.05, 0.05), limits = c(0, 1))
g1 / g2 / g3

# Approximate the Pareto front with a smoothed line using a Savitzky-Golay filter
Pfront.x1 = loess(x1 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                                x1 = filter(GPar.all, dist == 0)$x1))
Pfront.x2 = loess(x2 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                               x2 = filter(GPar.all, dist == 0)$x2))
Pfront.x3 = loess(x3 ~ theta, data = data.frame(theta = filter(GPar.all, dist == 0)$theta, 
                                               x3 = filter(GPar.all, dist == 0)$x3))

# Store the information in a dataframe for visualization
plt = data.frame(theta = seq(from = 0, to = 100, length.out = 100))
res1 = predict(object = Pfront.x1, newdata = plt)
res2 = predict(object = Pfront.x2, newdata = plt)
res3 = predict(object = Pfront.x3, newdata = plt)
plt$x1 = unname(res1); plt$x2 = unname(res2); plt$x3 = unname(res3)
# Check the Savitzky–Golay filter smoothing quality
gx1 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x1)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x1))
gx2 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x2)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x2))
gx3 = ggplot() +
  geom_path(plt, mapping = aes(x = theta, y = x3)) +
  geom_point(filter(GPar.all, dist == 0), mapping = aes(x = theta, y = x3))
gx1 / gx2 / gx3

# Apply the model to find the linear distance (regression)
GPar.all$x1.loess.Err = abs(GPar.all$x1 - predict(object = Pfront.x1, newdata = GPar.all$theta))
GPar.all$x2.loess.Err = abs(GPar.all$x2 - predict(object = Pfront.x2, newdata = GPar.all$theta))
GPar.all$x3.loess.Err = abs(GPar.all$x3 - predict(object = Pfront.x3, newdata = GPar.all$theta))

# Calculate the correlation coefficient of the log(objective distance) with the linear distance
x1.cor = cor(x = filter(GPar.all, dist > 0)$x1.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
x2.cor = cor(x = filter(GPar.all, dist > 0)$x2.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
x3.cor = cor(x = filter(GPar.all, dist > 0)$x3.loess.Err, 
             y = (filter(GPar.all, dist > 0)$dist), 
             method = 'pearson')
# Calculate the slope of the linear relationship
x1.slp = lm((dist) ~ x1.loess.Err, data = filter(GPar.all, dist > 0))
x2.slp = lm((dist) ~ x2.loess.Err, data = filter(GPar.all, dist > 0))
x3.slp = lm((dist) ~ x3.loess.Err, data = filter(GPar.all, dist > 0))
x1.slp = unname(x1.slp$coefficients[2]); x2.slp = unname(x2.slp$coefficients[2])
x3.slp = unname(x3.slp$coefficients[2])

sz = 3
# Store information in a dataframe for plotting
GPar.cor.plt = data.frame(obj.dist = rep(GPar.all$dist, 3),
                          inp.dist = c(GPar.all$x1.loess.Err, GPar.all$x2.loess.Err, GPar.all$x3.loess.Err),
                          var = c(rep('x1', nrow(GPar.all)), rep('x2', nrow(GPar.all)), rep('x3', nrow(GPar.all))),
                          region = rep(GPar.all$region, 3),
                          val = c(GPar.all$x1, GPar.all$x2, GPar.all$x3))
var.labs <- c(paste('x1, r = ', round(x1.cor, 3), '; slope = ', round(x1.slp, 3)), 
              paste('x2, r = ', round(x2.cor, 3), '; slope = ', round(x2.slp, 3)),
              paste('x3, r = ', round(x3.cor, 3), '; slope = ', round(x3.slp, 3)))
names(var.labs) <- c("x1", "x2", "x3")

ggplot(GPar.cor.plt) +
  geom_point(mapping = aes(x = inp.dist, y = (obj.dist), shape = region, color = val), size = sz) +
  facet_grid(~var, labeller = labeller(var = var.labs)) + 
  labs(x = 'Distance: Input Space', y = expression('log'[10]*' Distance: Objective Space'), shape = 'Priority',
       color = 'Input Value')

rm(g1, g2, g3, gx1, gx2, gx3, Pfront.x1, Pfront.x2, Pfront.x3, plt, GPar.cor.plt)

```


```{r Utopia distance: Marginalization}
# Use the final GP model with the full dataset
mod.rad = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'rad')
mod.ang = fill.sample.mod(GPar.data = GPar.all, input.name = c('x1', 'x2', 'x3'), output.name = 'theta')

# Obtain marginalized probabilities with a fine resolution grid (50 points). Calculate the integral with a Monte Carlo sampling of 500 samples each.
resolution = 50; MCsamp = 1500
x1.rng = range(GPar.all$x1); x2.rng = range(GPar.all$x2); x3.rng = range(GPar.all$x3)
x1.seq = seq(from = min(x1.rng), to = max(x1.rng), length.out = resolution)
x2.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)
x3.seq = seq(from = min(x3.rng), to = max(x3.rng), length.out = resolution)

Infer.x1 = data.frame(); Infer.x2 = data.frame(); Infer.x3 = data.frame()

for(i in 1:resolution){
  # x1
  fill.frame = data.frame(x1 = x1.seq[i], x2 = runif(n = MCsamp, min = min(x2.rng), max = max(x2.rng)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res1 = predict(object = mod.rad, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.ang, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * (1 - pnorm(q = 0, mean = res2$mean - 20, sd = res2$sd))
  Infer.x1 = rbind(Infer.x1, data.frame(x = x1.seq[i], prob = mean(fill.frame$p.del1), var = 'x1', cond = 'none'))
  
  # x2
  fill.frame = data.frame(x2 = x2.seq[i], x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res1 = predict(object = mod.rad, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.ang, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * (1 - pnorm(q = 0, mean = res2$mean - 20, sd = res2$sd))
  Infer.x2 = rbind(Infer.x2, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'none'))
  
  # x3
  fill.frame = data.frame(x3 = x3.seq[i], x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)),
                          x2 = runif(n = MCsamp, min = min(x2.rng), max = max(x2.rng)))
  res1 = predict(object = mod.rad, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.ang, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * (1 - pnorm(q = 0, mean = res2$mean - 20, sd = res2$sd))
  Infer.x3 = rbind(Infer.x3, data.frame(x = x3.seq[i], prob = mean(fill.frame$p.del1), var = 'x3', cond = 'none'))
}

ggplot() +
  geom_path(data = Infer.x1, mapping = aes(x = x, y = prob, color = var)) +
  geom_path(data = Infer.x2, mapping = aes(x = x, y = prob, color = var)) +
  geom_path(data = Infer.x3, mapping = aes(x = x, y = prob, color = var)) +
  labs(x = expression('x'), y = 'Probability of Acceptance', 
       subtitle = expression('Accept if r < 1 & > 80% f'[1]*' priority')) +
  scale_color_manual(name = 'Variable', values = c('x1' = 'red', 'x2' = 'blue', 'x3' = 'maroon'), 
                    labels = c('x1' = expression('x'[1]), 'x2' = expression('x'[2]),'x3' = expression('x'[3]))) +
  theme_bw()

```

Interestingly, while there are multiple peaks for $x_2$, it is only the peak on the right. This is due to the prioritization of $F_1$ compared to $F_2$ and not an issue with the model. The fact that $x_2$ and $x_3$ are treated differently is still an issue.

```{r Utopia distance: Partial Conditional Probabilities}
# Determining the ranges
# Function to find the optimal range given the probability of acceptance
p.lims = function(data.prob, p.target){
  # data.prob is a dataframe with variables x and prob, which are the values and probability of acceptance
  
  # Limits are the range where the probability is at least half the maximim
  # p.target = 0.5*max(data.prob$prob)
  
  # Initial limits
  x.lims = range(filter(data.prob, prob >= p.target)$x)
  
  # Linear interpolate to find the proper point, assuming that the limit is not already the minimum possible value
  if(x.lims[1] > min(data.prob$x)){
    pos = which.min(abs(data.prob$x - x.lims[1]))
    sub = data.prob[c(pos-1, pos), ]
    mod = lm(x~prob, data = sub)
    res = predict(object = mod, newdata = data.frame(prob = p.target))
    x.lims[1] = res
  }
  if(x.lims[2] < max(data.prob$x)){
    pos = which.min(abs(data.prob$x - x.lims[2]))
    sub = data.prob[c(pos, pos+1), ]
    mod = lm(x ~ prob, data = sub)
    res = predict(object = mod, newdata = data.frame(prob = p.target))
    x.lims[2] = res
    rm(mod)
  }
  return(x.lims)
}
x1.lims = p.lims(data.prob = Infer.x1, p.target = 0.5*max(Infer.x1$prob))
x3.lims = p.lims(data.prob = Infer.x3, p.target = 0.5*max(Infer.x3$prob))

## Given that x1 or x3 is optimal, find the next variable in the series: x2
resolution = 50; MCsamp = 1500
x2.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)

# Single conditional: x2|x1 or x2|x3
Infer.x2.x1 = data.frame(); Infer.x2.x3 = data.frame()

for(i in 1:resolution){
  # x2 | x1
  fill.frame = data.frame(x2 = x2.seq[i], x1 = runif(n = MCsamp, min = min(x1.lims), max = max(x1.lims)),
                          x3 = runif(n = MCsamp, min = min(x3.rng), max = max(x3.rng)))
  res1 = predict(object = mod.rad, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.ang, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * (1 - pnorm(q = 0, mean = res2$mean - 20, sd = res2$sd))
  Infer.x2.x1 = rbind(Infer.x2.x1, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'x1'))
  # x2 | x3
  fill.frame = data.frame(x2 = x2.seq[i], x3 = runif(n = MCsamp, min = min(x3.lims), max = max(x3.lims)),
                          x1 = runif(n = MCsamp, min = min(x1.rng), max = max(x1.rng)))
  res1 = predict(object = mod.rad, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.ang, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * (1 - pnorm(q = 0, mean = res2$mean - 20, sd = res2$sd))
  Infer.x2.x3 = rbind(Infer.x2.x3, data.frame(x = x2.seq[i], prob = mean(fill.frame$p.del1), var = 'x2', cond = 'x3'))
}

ggplot(rbind(Infer.x2.x3, Infer.x2.x1)) +
  geom_path(mapping = aes(x = x, y = prob, color = cond)) +
  labs(x = expression('x'[2]), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'),
       color = 'Given optimal') +
  theme_bw()

# Instead of a simple range, the multimodal peaks of these probability curves mean a simple min/max bound can be used. While a nearest-neighbor approximation would work, a faster solution is to find 3 separate ranges.
x2.lims.x3.rng2 = p.lims(data.prob = filter(Infer.x2.x3, x > 0.25, x < 0.75), 
                         p.target = max(Infer.x2.x3$prob)*0.5)
x2.lims.x3.rng3 = p.lims(data.prob = filter(Infer.x2.x3, x > 0.75), 
                         p.target = max(Infer.x2.x3$prob)*0.5)
x2.lims.x1.rng2 = p.lims(data.prob = filter(Infer.x2.x1, x > 0.25, x < 0.75), 
                         p.target = max(Infer.x2.x1$prob)*0.5)
x2.lims.x1.rng3 = p.lims(data.prob = filter(Infer.x2.x1, x > 0.75), 
                         p.target = max(Infer.x2.x1$prob)*0.5)
# The number of points to collect from each range is proportional to their relative widths

## Given that x1 or x3 is optimal, find the next variable in the series: x2
# resolution = 50; MCsamp = 1500
MCsamp.x2.x3.rng2 = round(1500*diff(x2.lims.x3.rng2)/
                            (diff(x2.lims.x3.rng1) + diff(x2.lims.x3.rng2) + diff(x2.lims.x3.rng3)))
MCsamp.x2.x3.rng3 = 1500 - MCsamp.x2.x3.rng2
MCsamp.x2.x1.rng2 = round(1500*diff(x2.lims.x1.rng2)/
                            (diff(x2.lims.x1.rng1) + diff(x2.lims.x1.rng2) + diff(x2.lims.x1.rng3)))
MCsamp.x2.x1.rng3 = 1500 - MCsamp.x2.x1.rng2

x1.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)
x3.seq = seq(from = min(x2.rng), to = max(x2.rng), length.out = resolution)

# Single conditional: x2|x1 or x2|x3
Infer.x3.x2.x1 = data.frame(); Infer.x1.x2.x3 = data.frame()
for(i in 1:resolution){
  # x3 | x2, x1
  x2.fill = c(runif(n = MCsamp.x2.x1.rng2, min = min(x2.lims.x1.rng2), max = max(x2.lims.x1.rng2)),
              runif(n = MCsamp.x2.x1.rng3, min = min(x2.lims.x1.rng3), max = max(x2.lims.x1.rng3)))
  fill.frame = data.frame(x2 = x2.fill, x1 = runif(n = MCsamp, min = min(x1.lims), max = max(x1.lims)),
                          x3 = x3.seq[i])
  res1 = predict(object = mod.rad, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.ang, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * (1 - pnorm(q = 0, mean = res2$mean - 20, sd = res2$sd))
  Infer.x3.x2.x1 = rbind(Infer.x3.x2.x1, data.frame(x = x3.seq[i], prob = mean(fill.frame$p.del1), 
                                                    var = 'x3', cond = 'x2, x1'))
  # x1 | x2, x3
  x2.fill = c(runif(n = MCsamp.x2.x3.rng2, min = min(x2.lims.x3.rng2), max = max(x2.lims.x3.rng2)),
              runif(n = MCsamp.x2.x3.rng3, min = min(x2.lims.x3.rng3), max = max(x2.lims.x3.rng3)))
  fill.frame = data.frame(x2 = x2.fill, x3 = runif(n = MCsamp, min = min(x3.lims), max = max(x3.lims)),
                          x1 = x1.seq[i])
  res1 = predict(object = mod.rad, newdata = fill.frame, type = 'UK')
  res2 = predict(object = mod.ang, newdata = fill.frame, type = 'UK')
  fill.frame$p.del1 = pnorm(q = 0, mean = res1$mean - 2, sd = res1$sd) * (1 - pnorm(q = 0, mean = res2$mean - 20, sd = res2$sd))
  Infer.x1.x2.x3 = rbind(Infer.x1.x2.x3, data.frame(x = x1.seq[i], prob = mean(fill.frame$p.del1), 
                                                    var = 'x1', cond = 'x2, x3'))
}

# Combine results for visualization
Infer.plt = rbind(Infer.x1, Infer.x2, Infer.x3, Infer.x2.x1, Infer.x2.x3, 
                  Infer.x1.x2.x3, Infer.x3.x2.x1);
write.csv(Infer.plt, 'Marginals_Accept_Radius.csv')
rm(res1, res2, x2.fill, fill.frame)
```



```{r}
Infer.plt = read.csv(file = 'Marginals_Accept_Radius.csv')

ggplot(filter(Infer.plt, cond == 'none')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(var))) +
  labs(x = expression('x'), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Variable') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()

ggplot(filter(Infer.plt, cond == 'x2, x3' | cond == 'x2, x1' | cond == 'none', var != 'x2')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(cond))) +
  facet_wrap(~var, nrow = 2) +
  labs(x = 'x', y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Partial Conditions') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()

ggplot(filter(Infer.plt, var == 'x2')) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(cond))) +
  labs(x = expression('x'[2]), y = 'Probability of Acceptance', subtitle = expression('Accept if '*delta*' < 1'), 
       color = 'Partial Conditions') +
  scale_y_continuous(expand = c(0, 0.05)) + scale_x_continuous(expand = c(0, 0)) +
  theme_bw()

```

## Comparison of selection criteria by their marginals

```{r}
Margin.del = read.csv(file = 'Marginals_Accept_Delta1.csv')
Margin.cut = read.csv(file = 'Marginals_Accept_Threshold.csv')
Margin.rad = read.csv(file = 'Marginals_Accept_Radius.csv')

Margin.del$criteria = 'Normalized Distance'
Margin.cut$criteria = 'Objective Value'
Margin.rad$criteria = 'Utopia Distance and F1 Priority'

Margin = rbind(Margin.del, Margin.cut, Margin.rad)

ggplot(Margin) +
  geom_path(mapping = aes(x = x, y = prob, color = as.factor(cond))) +
  facet_grid(var~criteria) + 
  labs(x = 'Input Value', y = 'Probability of Acceptance', subtitle = 'Candidate Screening', 
       color = 'Partial\nConditions') +
  scale_y_continuous(expand = c(0, 0.05)) + 
  scale_x_continuous(expand = c(0, 0.05), labels = c('0.0', '0.25', '0.5', '0.75', '1.0')) +
  theme_bw() + theme(panel.spacing.x = unit(0.5, "lines"))

```

