---
title: "CO2 Capture with Proton Coupled Electron Transfers - Preparation"
author: "Jonathan Boualavong"
output: html_notebook
---

<!-- output:    -->
<!--   md_document: -->
<!--     variant: markdown_github -->

# Description
This notebook performs preliminary calculations on a simulated CO2 capture process driven by PCET pH swings.
The work assumes that the redox molecule is a quinone (ie. a 2 electron/2 proton PCET process), and restricts the search to only combinations of properties that a quinone is likely to have.

Specifically, this particular notebook determines:

* the ranges of the variables based on existing data
* penalty functions for the energy and/or flux
* the energy and flux targets for refinement

# Code
## Initialization

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear the workspace and define the functions.

```{r Load Packages}
# Setup
rm(list = ls())
# Visualization
library(dplyr)
library(ggplot2)
library(patchwork)
# Parallel processing
library(parallel)
library(doParallel)
# Gaussian processes
library(GPareto)
library(DiceKriging)
library(DiceOptim)
# Optimization
library(GA)
```

## Parameter space
Data for restricting the quinone features is based on results from Huynh et al. J Am Chem Soc. 2016 December 14; 138(49): 15903–15910. doi:10.1021/jacs.6b05797.

Remove points that are not likely to be stable within the electrochemcial window of water. For the process:
Q + 2e- + 2H+ <-> QH2
We can roughly assume that the reduction reaction is competing with hydrogen evolution
2H+ + 2e- <-> H2
and the oxidation reaction is competing with oxygen evolution
2H2O + 4OH- <-> O2 + 4e-

Both of these reactions are pH dependent, so the cutoff values are not obvious. 
At the extreme, the reduction potential of hydrogen evolution will be at its highest (most likely to compete with the quinone reduction) at the lowest pH, which would typically be at the pH where carbonic acid makes up > 90% of the CO2 speciation (pH = 5.33).
Similarly, the reduction potential of oxygen evolution will be at its lowest at the highest pH, which would be just above the hydroquinone's buffer region (the higher of its pKas + 1).

Practically, the quinone electrochemistry has much faster kinetics than either gas evolution reaction in the absence of a specific water-splitting catalyst, so a tolerance of about 200 mV will be added to accommodate.

```{r}
# Load data and correlation plot package
quinone.data = read.csv(file = 'HuynhData.csv', skip = 1)

# Filter the data to only those whose reaction would be stable in water
## Hydrogen evolution
h2.evo = -59.2*1e-3 * 5.33
quinone.data = filter(quinone.data, E0.2 > h2.evo)

## Cutoff value for oxygen evolution
o2.evo = 1.229 + -59.2*1e-3*quinone.data$Pka.2+1
quinone.data = filter(quinone.data, E0.1 < o2.evo)

quinone.data

# Correlation plot between the E0 and pka values
cor.mat = matrix(data = rep(0, 16), nrow = 4)
for(i in seq(from = 6, to = 9, by = 1)){
  for(j in seq(from = i, to = 9, by = 1)){
    cor.mat[i-5,j-5] = cor(x = quinone.data[,i], y = quinone.data[,j])
  }
}
cor.mat

g1 = ggplot(quinone.data) +
  geom_point(mapping = aes(y = E0.1, x = E0.2)) +
  labs(subtitle = paste('r = ', round(cor.mat[1,2], 3))) 
g2 = ggplot(quinone.data) +
  geom_point(mapping = aes(y = E0.1, x = Pka.1)) +
  labs(subtitle = paste('r = ', round(cor.mat[1,3], 3)))
g3 = ggplot(quinone.data) +
  geom_point(mapping = aes(y = E0.1, x = Pka.2)) +
  labs(subtitle = paste('r = ', round(cor.mat[1,4], 3)))
g4 = ggplot(quinone.data) +
  geom_point(mapping = aes(y = E0.2, x = Pka.1)) +
  labs(subtitle = paste('r = ', round(cor.mat[2,3], 3)))
g5 = ggplot(quinone.data) +
  geom_point(mapping = aes(y = E0.2, x = Pka.2)) +
  labs(subtitle = paste('r = ', round(cor.mat[2,4], 3)))
g6 = ggplot(quinone.data) +
  geom_point(mapping = aes(y = Pka.1, x = Pka.2)) +
  labs(subtitle = paste('r = ', round(cor.mat[3,4], 3)))

(g1 + g2 + g3) / (plot_spacer() + g4 + g5) / (plot_spacer() + plot_spacer() + g6)
rm(g1, g2, g3, g4, g5, g6)
rm(h2.evo, i, j, o2.evo, cor.mat)
```

While all four variables are strongly co-correlated, this is largely irrelevant because the thermodynamic and kinetic analyses do not rely on the reduction potential besides assuming that gas evolution does not occur.
There is a Bronsted-like relationship between the reduction potential and the reaction rate of the deprotonated hydroquinone nucleophilically attacking the CO2 [Simpson & Durand 1990, doi: 10.1016/0013-4686(90)85012-C], but this is not likely to be the dominant mechanism because the reaction with OH- is approximately 10 to 100 times faster in water.
To determine which pKa will be the free variable and which will be represented by an error term of the linear regression, the relative normalized standard deviations of the errors were compared. 

```{r}
print('pka2 as free variable, pKa1 as the solved variable')
mod1 = lm(Pka.1 ~ Pka.2, data = quinone.data)
sd(mod1$residuals[abs(mod1$residuals) < 10]) / diff(range(quinone.data$Pka.1))
  
print('pka1 as free variable, pKa2 as the solved variable')
mod2 = lm(Pka.2 ~ Pka.1, data = quinone.data)
sd(mod2$residuals[abs(mod2$residuals) < 10]) / diff(range(quinone.data$Pka.2))

x = c(unname(mod1$residuals), unname(mod2$residuals))
var = c(rep('pka1', length(mod1$residuals)), rep('pka2', length(mod1$residuals)))
ggplot(data.frame(x, var)) +
  geom_density(mapping = aes(x = x, color = var)) +
  scale_color_manual(labels = c('pka1' = 'pka1 = f(pka2)', 'pka2' = 'pka2 = f(pka1)'),
                     values = c('pka1' = 'red', 'pka2' = 'blue'), name = '') +
  labs(x = 'Residual', y = 'Probability Density')

# Determine the value for the standard deviation that should be used to encompass 98% of the search space
q1 = quantile(mod2$residuals, probs = c(0.01))
q2 = quantile(mod2$residuals, probs = c(0.99))
# Plot the data and the search space
fit.ln = data.frame(Pka.1 = seq(from = -8.33, to = 13.41, length.out = 3))
fit.ln$Pka.2 = predict(object = mod2, newdata = fit.ln)
ggplot() +
  geom_point(quinone.data, mapping = aes(x = Pka.1, y = Pka.2), color = 'blue', alpha = 0.5) +
  geom_line(fit.ln, mapping = aes(x = Pka.1, y = Pka.2), color = 'black', linetype = 1) +
  geom_line(fit.ln, mapping = aes(x = Pka.1, y = Pka.2+q2), color = 'black', linetype = 2) +
  geom_line(fit.ln, mapping = aes(x = Pka.1, y = Pka.2+q1), color = 'black', linetype = 2) +
  geom_line(fit.ln, mapping = aes(x = Pka.1, y = Pka.1), color = 'red', linetype = 2) +
  geom_line(fit.ln, mapping = aes(x = Pka.1, y = Pka.1+q2), color = 'red', linetype = 2) +
  labs(title = expression('Known Quinone p'*italic(K)*''[a]*'s'),
       y = expression('p'*italic(K)*''['a,2']),
       x = expression('p'*italic(K)*''['a,1']))
q1
q2
rm(fit.ln, x, var)

```

The variance alone show very little difference between the choice, which pKa1 being the free variable having a slightly better response.
This is confirmed by the distribution of the residuals (omitting the single outlier), which shows that having pKa1 as the free variable gives a distribution closer to a normal distribution.
Therefore, the range of pKas is:

pKa1: -8.33 to 13.41
pKa2 = f(pKa1) + error

While the error for pKa2 is nearly Gaussian in shape, the mathematical description works better if it is sampled from a uniform distribution. From the data, 98% of the data is captured within an error of -3.9 to +5.5.

This range of pKas has 2 problems:
* It is very unlikely that the second pKa is lower than the first. Only one measurement violates this criteria (ie. is below red dotted line) within measurement error.
* The pH of the process is not likely to extend below 3 because the primary acid in question is carbonic acid. This means that pKa values below 2 are effectively the same and do not need to be sampled further. Therefore, the lower bound for pKa1 can be increased to reduce the search space.

The refined search space is:

pKa1: 0 to 13.41
pKa2 = pKa1 + error
error ~ unif(0, 5.5)

This construction reduces the size of the search space, and thus requires fewer points to characterize its dynamics.

## Objective Functions

The objective function for energy demand solves the set of equilibrium equations across the range of charge and gas transfers based on four state variables: 
total dissolved inorganic carbon (DIC), state of charge (xA), partial pressure of CO2 (pCO2), and solution pH.

The minimum energy demand assumes all charge is passed at the Nernst potential, which is updated as charge passes through the system.
The energy demand assumes anti-symmetric operation, ie. quinone reduction at the cathode and hydroquinone oxidation at the anode.
Charge balance of the anolyte and catholyte are assumed to be the result of the background electrolyte travelling across an ion selective membrane.
The gas transfers are assumed to be separate stages from the electrochemical stages, purely for the sake of simplicity. 
This estimate for the minimum energy is a slight overestimate because of over-pressurization of the CO2; coupling the gas transfer steps with the appropriate electrochemical steps decreases the minimum energy by approximately a factor of 2.
The function can accommodate feed CO2 gases of any partial pressure, but this study is interested in 3 applications: coal flue gas (15v% feed to 1.5v% lean), air revitalization (2000 ppm to 1000 ppm), and direct air capture (400 ppm to 250 ppm).

This code is broken down into explicit functions and derived functions.
Explicit functions are a series of sub-functions which solve for one of the four state variables using knowledge of the other three state variables and the solution conditions. 
These functions solve the set of chemical equilibrium, mass, and charge balance equations for the bulk solution.
Derived functions use the information from the explicit functions to determine relevant information for determining the energy demand and CO2 flux.

For the purpose of generalization, these equations are written with the variables 'beta1' and 'beta2' which describe the deprotonated hydroquinone's affinity for CO2, forming an organic carbonate. 
This species is ignored in this particular notebook for the above-stated reason (slow kinetics), and therefore both variables are set to 0.
These variables are included because other compounds have been proposed to capture CO2 primarily through that mechanism, and thus they could also be studied with this script.

```{r PCET Explicit functions}
# Direct explicit functions
# Functions are named with the output variable first, then all relevant inputs
DIC.xA.pCO2.pH.A.k.beta = function(xA, pCO2, pH, A.tot, k1, k2, beta1, beta2){
  # Constants: carbonate and water chemistry 
  kH = 3.4e-2; # M/atm
  kc1 = 10^-6.3
  kc2 = 10^-10.3
  kw = 1e-14
  
  # Proton concentration
  H = 10^-pH
  
  # Inorganic carbonate
  CO3.free = kH * pCO2 * (H^2 + kc1 * H + kc1 * kc2) / H^2
  
  # Bound carbon
  CO2.bound = A.tot*xA *k1*k2*(beta1*pCO2 + 2*beta2*pCO2^2)/((1 + beta1*pCO2 + beta2*pCO2^2)*k1*k2 + k1*H + H^2)
  
  return(CO3.free + CO2.bound)
}

pH.xA.pCO2.A.k.beta.Na = function(xA, P, At, k1, k2, beta1, beta2, Na){
  # Constants: carbonate and water chemistry 
  kH = 3.4e-2; # M/atm
  kc1 = 10^-6.3
  kc2 = 10^-10.3
  kw = 1e-14
  
  # Polynomial root
  x5 = 1
  x4 = k1 + Na + 2*At*xA 
  x3 = k1*k2 - kw + k1*Na + beta1*k1*k2*P - kc1*kH*P +
      beta2*k1*k2*P^2 + 2*At*k1*xA - 2*At*k2*xA
  x2 = (-k1)*kw + k1*k2*Na - k1*kc1*kH*P - 2*kc1*kc2*kH*P + beta1*k1*k2*Na*P + beta2*k1*k2*Na*P^2 -
      2*At*k1*k2*xA + 2*At*beta1*k1*k2*P*xA + 2*At*beta2*k1*k2*P^2*xA
  x1 = (-k1)*k2*kw - k1*k2*kc1*kH*P - 2*k1*kc1*kc2*kH*P - beta1*k1*k2*kw*P -
      beta1*k1*k2*kc1*kH*P^2 - beta2*k1*k2*kw*P^2 - beta2*k1*k2*kc1*kH*P^3
  x0 = - 2*k1*k2*kc1*kc2*kH*P - 2*beta1*k1*k2*kc1*kc2*kH*P^2 -
     2*beta2*k1*k2*kc1*kc2*kH*P^3
  roots = polyroot(c(x0, x1, x2, x3, x4, x5))
  
  # Only the real and positive roots
  H = roots[abs(Im(roots)) < 1e-8]
  H = Re(H[Re(H) > 0])
  
  # It is possible for multiple roots to satisfy the solution. Typical pH is going to be the one closest to 7-8
  # H = H[which.min(abs(-log10(H) - 7))]

  return(-log10(H[1]))
}

pCO2.xA.pH.A.k.beta.Na = function(xA, pH, At, k1, k2, beta1, beta2, Na, pCO2.prev){
  # Constants: carbonate and water chemistry 
  kH = 3.4e-2; # M/atm
  kc1 = 10^-6.3
  kc2 = 10^-10.3
  kw = 1e-14
  # Proton concentration
  H = 10^-pH
  
  # Polynomial root
  x3 = (-beta2)*H*k1*k2*kc1*kH - 2*beta2*k1*k2*kc1*kc2*kH
  x2 = beta2*H^3*k1*k2 - beta1*H*k1*k2*kc1*kH - 2*beta1*k1*k2*kc1*kc2*kH -
      beta2*H*k1*k2*kw + beta2*H^2*k1*k2*Na + 2*At*beta2*H^2*k1*k2*xA
  x1 = beta1*H^3*k1*k2 - H^3*kc1*kH - H^2*k1*kc1*kH - H*k1*k2*kc1*kH - 2*H^2*kc1*kc2*kH - 2*H*k1*kc1*kc2*kH -
      2*k1*k2*kc1*kc2*kH - beta1*H*k1*k2*kw + beta1*H^2*k1*k2*Na +
      2*At*beta1*H^2*k1*k2*xA
  x0 = H^5 + H^4*k1 + H^3*k1*k2 - H^3*kw - H^2*k1*kw - H*k1*k2*kw +
      H^4*Na + H^3*k1*Na + H^2*k1*k2*Na + 2*At*H^4*xA + 2*At*H^3*k1*xA -
      2*At*H^3*k2*xA - 2*At*H^2*k1*k2*xA
  roots = polyroot(c(x0, x1, x2, x3))
  
  # Only the real and positive roots
  pCO2 = roots[abs(Im(roots)) < 1e-8]
  pCO2 = Re(pCO2[Re(pCO2) > 0])
  # There are cases of multiepl roots. Find the one that is closest to the previous known value
  pCO2 = pCO2[which.min(abs(log10(pCO2) - log10(pCO2.prev)))]
  
  return(pCO2)
}

pH.DIC.xA.pCO2.A.k.beta = function(DIC, xA, P, At, k1, k2, beta1, beta2){
  # Constants: carbonate and water chemistry 
  kH = 3.4e-2; # M/atm
  kc1 = 10^-6.3
  kc2 = 10^-10.3
  kw = 1e-14
  
  # Polynomial root
  x4 = (DIC - kH*P)
  x3 = (DIC*k1 - k1*kH*P - kc1*kH*P)
  x2 = (DIC*k1*k2 + beta1*DIC*k1*k2*P - k1*k2*kH*P - k1*kc1*kH*P - kc1*kc2*kH*P + beta2*DIC*k1*k2*P^2 - 
    beta1*k1*k2*kH*P^2 - beta2*k1*k2*kH*P^3 - At*beta1*k1*k2*P*xA - 2*At*beta2*k1*k2*P^2*xA)
  x1 = ((-k1)*k2*kc1*kH*P - k1*kc1*kc2*kH*P - beta1*k1*k2*kc1*kH*P^2 - 
        beta2*k1*k2*kc1*kH*P^3)
  x0 = (-k1)*k2*kc1*kc2*kH*P - beta1*k1*k2*kc1*kc2*kH*P^2 - beta2*k1*k2*kc1*kc2*kH*P^3
  roots = polyroot(c(x0, x1, x2, x3, x4))
  
  # Only the real and positive roots
  H = roots[abs(Im(roots)) < 1e-8]
  H = Re(H[Re(H) > 0])
  return(-log10(H))
}

pCO2.DIC.xA.pH.A.k.beta = function(DIC, xA, pH, At, k1, k2, beta1, beta2){
  # Constants: carbonate and water chemistry 
  kH = 3.4e-2; # M/atm
  kc1 = 10^-6.3
  kc2 = 10^-10.3
  kw = 1e-14
  
  H = 10^-pH
  
  # Polynomial root
  x3 = ((-beta2)*H^2*k1*k2*kH - beta2*H*k1*k2*kc1*kH - beta2*k1*k2*kc1*kc2*kH)
  x2 = (beta2*DIC*H^2*k1*k2 - beta1*H^2*k1*k2*kH - beta1*H*k1*k2*kc1*kH - 
        beta1*k1*k2*kc1*kc2*kH - 2*At*beta2*H^2*k1*k2*xA)
  x1 = (beta1*DIC*H^2*k1*k2 - H^4*kH - H^3*k1*kH - H^2*k1*k2*kH - H^3*kc1*kH - 
        H^2*k1*kc1*kH - H*k1*k2*kc1*kH - H^2*kc1*kc2*kH - H*k1*kc1*kc2*kH - 
        k1*k2*kc1*kc2*kH - At*beta1*H^2*k1*k2*xA)
  x0 = DIC*H^4 + DIC*H^3*k1 + DIC*H^2*k1*k2
  roots = polyroot(c(x0, x1, x2, x3))
  
  # Only the real and positive roots
  pCO2 = roots[abs(Im(roots)) < 1e-8]
  pCO2 = Re(pCO2[Re(pCO2) > 0])
  return(pCO2)
}

# There are cases in the process where both pH and pCO2 are unknown. 
# For those cases, both variables can be solved togther, but it leads to coupled nonlinear root finding problems. 
# Initial testing of the equations has found that using an initial guess of pH (such as the pH at the immediately previous state of charge) leads to a good enough estimate of the pH to solve pCO2.
pH.it.guess.DIC.At.k.beta = function(pH.guess, xA.next, DIC, A.tot, k1, k2, beta1, beta2, Na){
  # Iterates to solve the pH and pCO2 at the next electrochemical time step, 
  # given xA and DIC and an initial guess (the pH at the previous time step)
  pCO2.it = c(); pH.it = c(pH.guess)
  pCO2.it = pCO2.DIC.xA.pH.A.k.beta(DIC = DIC, xA = xA.next, pH = pH.it, At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2)
  for(n in 2:74){
    pH.it[n] = pH.xA.pCO2.A.k.beta.Na(xA = xA.next, P = pCO2.it[n - 1], At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
    pCO2.it[n] = pCO2.DIC.xA.pH.A.k.beta(DIC = DIC, xA = xA.next, pH = pH.it[n], At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2)
  } 
  n = 7:5
  pH.it[n] = pH.xA.pCO2.A.k.beta.Na(xA = xA.next, P = pCO2.it[n - 1], At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  # Due to some oscillatory instabilities under specific conditions, take the last 25 and use the value that is closest to the guess
  pH.res = pH.it[50:75]
  pH.res = pH.res[which.min(abs(pH.res) - pH.guess)]
  return(pH.res)
}
```

```{r PCET Derived Functions: Process Conditions}
# Derived functions
# DIC difference: CO2/L*cycle - this is a good first check for the condition to ensure that CO2 is, in fact, captured, represented by a positive value.
DIC.diff = function(Na, A, beta1, beta2, k1, k2, pCO2.in, pCO2.out){
  # Constants
  xA.lim = c(0.025, 0.975)
  # pCO2.in = 0.1; pCO2.out = 1
  
  # Absorption: low P, high xA
  start.soln = data.frame(p.CO2 = pCO2.in, xA = max(xA.lim))
  start.soln$pH = pH.xA.pCO2.A.k.beta.Na(xA = start.soln$xA, P = start.soln$p.CO2, 
                                     At = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  start.soln$DIC = DIC.xA.pCO2.pH.A.k.beta(xA = start.soln$xA, pCO2 = start.soln$p.CO2, pH = start.soln$pH, 
                                       A.tot = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2)
  
  # Desorption: high P, low xA
  stop.soln = data.frame(p.CO2 = pCO2.out, xA = min(xA.lim))
  stop.soln$pH = pH.xA.pCO2.A.k.beta.Na(xA = stop.soln$xA, P = stop.soln$p.CO2, 
                                     At = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  stop.soln$DIC = DIC.xA.pCO2.pH.A.k.beta(xA = stop.soln$xA, pCO2 = stop.soln$p.CO2, pH = stop.soln$pH, 
                                       A.tot = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2)
  
  # Calculate the difference
  DIC.diff = start.soln$DIC - stop.soln$DIC
  return(DIC.diff)
}

# Minimum partial pressure of the lean gas
pCO2.lean = function(Na, A, beta1, beta2, k1, k2, pCO2.out){
  # Constants
  xA.lim = c(0.025, 0.975)
  
  # Calculate the DIC of the outlet after complete desorption: high P, low xA
  stop.soln = data.frame(p.CO2 = pCO2.out, xA = min(xA.lim))
  stop.soln$pH = pH.xA.pCO2.A.k.beta.Na(xA = stop.soln$xA, P = stop.soln$p.CO2, 
                                     At = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  stop.soln$DIC = DIC.xA.pCO2.pH.A.k.beta(xA = stop.soln$xA, pCO2 = stop.soln$p.CO2, pH = stop.soln$pH, 
                                       A.tot = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2)
  
  # Calculate the pCO2 when fully reduced, holding DIC constant. Due to the need for a previous case, run in ~5 steps
  out.soln = data.frame(DIC = stop.soln$DIC, xA = seq(from = min(xA.lim), to = max(xA.lim), length.out = 5))
  # Loop the pH and pCO2 simultaneously
  loop.pH = pH.it.guess.DIC.At.k.beta(pH.guess = stop.soln$pH[1], xA.next = out.soln$xA[1], DIC = out.soln$DIC[1],
                                      A.tot = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  loop.pCO2 = pCO2.xA.pH.A.k.beta.Na(xA = out.soln$xA[1], pH = loop.pH[1],
                                     At = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na, 
                                     pCO2.prev = stop.soln$p.CO2)
  for(i in 2:5){
    loop.pH[i] = pH.it.guess.DIC.At.k.beta(pH.guess = loop.pH[i-1], xA.next = out.soln$xA[i], DIC = out.soln$DIC[i],
                                        A.tot = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
    loop.pCO2[i] = pCO2.xA.pH.A.k.beta.Na(xA = out.soln$xA[i], pH = loop.pH[i],
                                       At = A, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na, 
                                       pCO2.prev = loop.pCO2[i-1])
    
  }
  return(loop.pCO2[i])
}

```


Penalty function: logistic weighting function such that for values where 90% of the CO2 is captured, the weight is 1, but when less CO2 is captured, the weight increases based on the relative change on the minimum work of separation.
The hyperparameters L, k, and x0 of the logistic component of the weighting function were tuned by fitting to a variety of minimum lean gas pressures on the range of 0.016 to 2.5 atm and then selected as the modal value.
The logistic function was tuned such that the growth rate steepness captured the range of 0 to 90% capture; when no CO2 could be captured, the weight is applied fully.

A penalty function is not necessary for the flux because insufficient capture would manifest as negative fluxes. It may still show up in the Pareto frontier, but it can easily be filtered out, unlike the cases with the energy demand.

Further tuning of the exact value of L is based on the minimumm energy demand for the specific lean gas minimum.

```{r}
GPar.all = read.csv(file = 'GPar_WeightTuningSet.csv')

# Original weighting function: adjust by the minimum energy demand, simplified
weight.fun = function(pCO2.lean){
  # Maximum weight
  weight.max = log(1/10) / log(pCO2.lean/0.15)
  # Logistic function
  L = weight.max - 0.98
  k = 267; x0 = 0.071
  # data.frame(weight.max)
  return(L/(1 + exp(-k * (pCO2.lean - x0))) + 1)
}

# Calculate weight
GPar.all$weight = weight.fun(GPar.all$pCO2.lean)

ggplot(filter(GPar.all, Energy.kJ.mol*weight < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = weight)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Simplified Weight')
ggplot(filter(GPar.all, Energy.kJ.mol*weight < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = Energy.kJ.mol)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Unweighted Energy')
ggplot(filter(GPar.all, Energy.kJ.mol*weight < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = Energy.kJ.mol*weight)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Simple Weighted Energy')


```

Simple weighted energy is not enough of a penalty; the minimum energy for systems that do not capture >90% of the CO2 are still showing lower energy demands. 

Using the complete expression for minimum energy demand instead of the simplified form, which makes a number of assumptions about negliglbe terms.

Minimum energy demand:
$$ RT \sum [n_{CO_2} \ ln(y_{CO_2}) +  n_{-CO_2} \ ln(y_{-CO_2})]_{outlet} - [n_{CO_2} \ ln(y_{CO_2}) +  n_{-CO_2} \ ln(y_{-CO_2})]_{inlet}$$

Since the concern is only the ratio for the weighting factor, then can assume the $RT$ term cancels.

The inlet term is constant at 0.15 atm and the reference point is 90% reduction in the partial pressure in the lean gas.
The calculation is based on mass balance, assuming that the volume adjusted to maintain a total pressure of 1 atm.

Assuming 1 total mole of gas is processed at the reference point:
* Inlet: 0.15 mol CO2, 0.85 mol not CO2
* Lean gas: 0.85 mol not CO2, (0.015*0.85)/(1 - 0.015) mol CO2
* Enriched gas: 1 - (0.015*0.85)/(1 - 0.015) mol CO2, 0.1% not CO2

The lean gas and enriched gas will change according to the system with a similar mass balance.

```{r}
weight.fun2 = function(pCO2.lean){
  # Ideal
  n.inlet = c(0.15, 0.85)
  n.lean = c(0.85, 0.015*0.85/(1 - 0.015))
  n.enrich = c(0.001*(1 - 0.015*0.85/(1 - 0.015)), 1 - 0.015*0.85/(1 - 0.015))
  
  E.ideal = sum(n.enrich*log(n.enrich/sum(n.enrich)) + 
                  n.lean*log(n.lean/sum(n.lean)) - 
                  n.inlet*log(n.inlet/sum(n.inlet)))

  # Actual: separate into 3 cases:
  E.tru = rep(x = 0, times = length(pCO2.lean))
  # Third case: if the lean gas pressure is above 1, i.e. it pressurized
  pos3 = (pCO2.lean >= 0.99)
  # Set the lean gas pressure to 0.999, 
  # then multiply the weight by the actual pressure to correct the energy; 
  # since the weight is divided by this energy, this means dividing by the pressure
  set.lean = 0.999
  n.enrich.co2 = (set.lean - 0.15)/(1 - set.lean)
  n.lean = n.enrich.co2 + 0.15
  n.enrich.gas = 0.001*n.enrich.co2
  E.tru[pos3] = (- sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))) / pCO2.lean[pos3]

  # Second case: if the lean gas pressure is between 0.15 and 1, 
  # i.e. the CO2 was moved from the pure gas to the lean gas
  pos2 = (pCO2.lean >= 0.15 & pCO2.lean < 0.99)
  # For the mass balance to work, gas must have moved from the enriched stream to the lean gas
  n.enrich.co2 = (pCO2.lean[pos2] - 0.15)/(1 - pCO2.lean[pos2])
  n.lean = n.enrich.co2 + 0.15
  n.enrich.gas = 0.001*n.enrich.co2
  E.tru[pos2] = - sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))
  
  # First case: if the lean gas pressure is less than 0.15, i.e. some amount of capture happened
  pos1 = (pCO2.lean < 0.15)
  # Mathematically identical to the lean gas case, just adjusting the lean gas and enriched gas mass balance
  n.lean = pCO2.lean[pos1]*0.85/(1 - pCO2.lean[pos1])
  n.enrich.co2 = 0.15 - n.lean
  n.enrich.gas = 0.001*n.enrich.co2
  
  E.tru[pos1] = - sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))
  
  # Maximum weight
  weight.max = E.ideal/E.tru

  # Logistic function
  L = weight.max - 0.98
  k = 267; x0 = 0.071
  # data.frame(weight.max)
  return(L/(1 + exp(-k * (pCO2.lean - x0))) + 1)
}

test.pco2 = 10^seq(from = -10, to = 2, by = 0.1)
weight.test = weight.fun2(test.pco2)
class = rep(0, length(test.pco2)); class[test.pco2 >= 0.15] = 1; class[test.pco2 >= 1] = 2
ggplot(filter(data.frame(x = test.pco2, y = weight.test, class) )) +
  geom_point(mapping = aes(x = x, y = y, color = (x < 0.015))) +
  scale_x_log10() + facet_wrap(~class, scales = 'free')
rm(test.pco2, weight.test, class)

# Calculate weight
GPar.all$weight2 = weight.fun2(GPar.all$pCO2.lean)

ggplot(filter(GPar.all, Energy.kJ.mol*weight2 < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = weight2)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Complete Weight')
ggplot(filter(GPar.all, Energy.kJ.mol*weight2 < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = Energy.kJ.mol)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Unweighted Energy')
ggplot(filter(GPar.all, Energy.kJ.mol*weight2 < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = Energy.kJ.mol*weight2)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Complete Weighted Energy')

```

While better, using the complete energy is not fixed upon this correction in that the minimum energy is still at a value where the flux would be negative. Amplifying an additional multiplicative factor to amplify the weight:

```{r}
weight.fun3 = function(pCO2.lean){
  # Ideal
  n.inlet = c(0.15, 0.85)
  n.lean = c(0.85, 0.015*0.85/(1 - 0.015))
  n.enrich = c(0.001*(1 - 0.015*0.85/(1 - 0.015)), 1 - 0.015*0.85/(1 - 0.015))
  
  E.ideal = sum(n.enrich*log(n.enrich/sum(n.enrich)) + 
                  n.lean*log(n.lean/sum(n.lean)) - 
                  n.inlet*log(n.inlet/sum(n.inlet)))

  # Actual: separate into 3 cases:
  E.tru = rep(x = 0, times = length(pCO2.lean))
  # Third case: if the lean gas pressure is above 1, i.e. it pressurized
  pos3 = (pCO2.lean >= 0.99)
  # Set the lean gas pressure to 0.999, 
  # then multiply the weight by the actual pressure to correct the energy; 
  # since the weight is divided by this energy, this means dividing by the pressure
  set.lean = 0.999
  n.enrich.co2 = (set.lean - 0.15)/(1 - set.lean)
  n.lean = n.enrich.co2 + 0.15
  n.enrich.gas = 0.001*n.enrich.co2
  E.tru[pos3] = (- sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))) / pCO2.lean[pos3]

  # Second case: if the lean gas pressure is between 0.15 and 1, 
  # i.e. the CO2 was moved from the pure gas to the lean gas
  pos2 = (pCO2.lean >= 0.15 & pCO2.lean < 0.99)
  # For the mass balance to work, gas must have moved from the enriched stream to the lean gas
  n.enrich.co2 = (pCO2.lean[pos2] - 0.15)/(1 - pCO2.lean[pos2])
  n.lean = n.enrich.co2 + 0.15
  n.enrich.gas = 0.001*n.enrich.co2
  E.tru[pos2] = - sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))
  
  # First case: if the lean gas pressure is less than 0.15, i.e. some amount of capture happened
  pos1 = (pCO2.lean < 0.15)
  # Mathematically identical to the lean gas case, just adjusting the lean gas and enriched gas mass balance
  n.lean = pCO2.lean[pos1]*0.85/(1 - pCO2.lean[pos1])
  n.enrich.co2 = 0.15 - n.lean
  n.enrich.gas = 0.001*n.enrich.co2
  
  E.tru[pos1] = - sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))
  
  # Maximum weight
  weight.max = E.ideal/E.tru

  # Logistic function
  L = weight.max - 0.98
  k = 267; x0 = 0.071
  # data.frame(weight.max)
  return(25*L/(1 + exp(-k * (pCO2.lean - x0))) + 1)
}

test.pco2 = 10^seq(from = -10, to = 2, by = 0.1)
weight.test = weight.fun2(test.pco2)
class = rep(0, length(test.pco2)); class[test.pco2 >= 0.15] = 1; class[test.pco2 >= 1] = 2
ggplot(filter(data.frame(x = test.pco2, y = weight.test, class) )) +
  geom_point(mapping = aes(x = x, y = y, color = (x < 0.015))) +
  scale_x_log10() + facet_wrap(~class, scales = 'free')
rm(test.pco2, weight.test, class)

# Calculate weight
GPar.all$weight3 = weight.fun3(GPar.all$pCO2.lean)

ggplot(filter(GPar.all, Energy.kJ.mol*weight3 < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = weight3)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Amplified Weight')
ggplot(filter(GPar.all, Energy.kJ.mol*weight3 < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = Energy.kJ.mol)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Unweighted Energy')
ggplot(filter(GPar.all, Energy.kJ.mol*weight3 < 100)) +
  geom_point(mapping = aes(x = pCO2.lean, y = Energy.kJ.mol*weight3)) +
  facet_grid(~(pCO2.lean >= 0.015), scales = 'free_x') +
  scale_x_log10() + labs(y = 'Amplified Weighted Energy')

```

Multiplying the logarithmic term by a factor of 25 appears to be sufficiently large to adjust the energies without overshooting the weight.

```{r}
rm(weight.fun, weight.fun2, weight.fun3, GPar.all)
```

Applying the penalty function directly to energy demand

```{r PCET Derived Functions: Energy Demand}
weight.fun = function(pCO2.lean){
  # Ideal
  n.inlet = c(0.15, 0.85)
  n.lean = c(0.85, 0.015*0.85/(1 - 0.015))
  n.enrich = c(0.001*(1 - 0.015*0.85/(1 - 0.015)), 1 - 0.015*0.85/(1 - 0.015))
  
  E.ideal = sum(n.enrich*log(n.enrich/sum(n.enrich)) + 
                  n.lean*log(n.lean/sum(n.lean)) - 
                  n.inlet*log(n.inlet/sum(n.inlet)))

  # Actual: separate into 3 cases:
  E.tru = rep(x = 0, times = length(pCO2.lean))
  # Third case: if the lean gas pressure is above 1, i.e. it pressurized
  pos3 = (pCO2.lean >= 0.99)
  # Set the lean gas pressure to 0.999, 
  # then multiply the weight by the actual pressure to correct the energy; 
  # since the weight is divided by this energy, this means dividing by the pressure
  set.lean = 0.999
  n.enrich.co2 = (set.lean - 0.15)/(1 - set.lean)
  n.lean = n.enrich.co2 + 0.15
  n.enrich.gas = 0.001*n.enrich.co2
  E.tru[pos3] = (- sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))) / pCO2.lean[pos3]

  # Second case: if the lean gas pressure is between 0.15 and 1, 
  # i.e. the CO2 was moved from the pure gas to the lean gas
  pos2 = (pCO2.lean >= 0.15 & pCO2.lean < 0.99)
  # For the mass balance to work, gas must have moved from the enriched stream to the lean gas
  n.enrich.co2 = (pCO2.lean[pos2] - 0.15)/(1 - pCO2.lean[pos2])
  n.lean = n.enrich.co2 + 0.15
  n.enrich.gas = 0.001*n.enrich.co2
  E.tru[pos2] = - sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))
  
  # First case: if the lean gas pressure is less than 0.15, i.e. some amount of capture happened
  pos1 = (pCO2.lean < 0.15)
  # Mathematically identical to the lean gas case, just adjusting the lean gas and enriched gas mass balance
  n.lean = pCO2.lean[pos1]*0.85/(1 - pCO2.lean[pos1])
  n.enrich.co2 = 0.15 - n.lean
  n.enrich.gas = 0.001*n.enrich.co2
  
  E.tru[pos1] = - sum(n.inlet*log(n.inlet/sum(n.inlet))) +
    0.85*log(0.85/(n.lean + 0.85)) +
    n.enrich.gas*log(n.enrich.gas/(n.enrich.gas + n.enrich.co2)) + 
    n.enrich.co2*log(n.enrich.co2/(n.enrich.gas + n.enrich.co2)) + 
    n.lean*log(n.lean/(n.lean + 0.85))
  
  # Maximum weight
  weight.max = E.ideal/E.tru

  # Logistic function
  L = weight.max - 0.98
  k = 267; x0 = 0.071
  # data.frame(weight.max)
  return(25*L/(1 + exp(-k * (pCO2.lean - x0))) + 1)
}

# Total energy demand - 4-stage process for simplicity
Energy.tot = function(k1, k2, beta1, beta2, A.tot, Na, pCO2.in, pCO2.out){
  # Constants
  z = 2; R = 8.314; T = 298; F = 96485; resolution = 151;
  # pCO2.in = 0.1; pCO2.out = 1
  xA.lim = c(0.025, 0.975)
  
  # 1 -> 2: Electrochemical oxidation (xA decrease to endpoint), constant DIC
  # Starting solution for initial guess: low P, high xA
  start.soln = data.frame(p.CO2 = pCO2.in, xA = max(xA.lim))
  start.soln$pH = pH.xA.pCO2.A.k.beta.Na(xA = start.soln$xA, P = start.soln$p.CO2, 
                                       At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  start.soln$DIC = DIC.xA.pCO2.pH.A.k.beta(xA = start.soln$xA, pCO2 = start.soln$p.CO2, pH = start.soln$pH, 
                                         A.tot = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2)
  # Anode progress
  E.anode = data.frame(DIC = start.soln$DIC, xA = seq(from = start.soln$xA[1], to = min(xA.lim), length.out = resolution))
  # Loop to solve the ieration function
  loop = pH.it.guess.DIC.At.k.beta(pH.guess = start.soln$pH[1], xA.next = E.anode$xA[1], DIC = E.anode$DIC[1], 
                                       A.tot = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  for(i in 2:length(E.anode$DIC)){
    loop = c(loop, pH.it.guess.DIC.At.k.beta(pH.guess = loop[i-1], xA.next = E.anode$xA[i], DIC = E.anode$DIC[i], 
                                         A.tot = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na))
  }
  # Some iterations don't converge completely, leading to single points that deviated from the rest of the curve. This is characterized by a single point that is a local maxima or minimum. Endpoints are asusmed to be good
  loop.check.left = loop[1:(resolution-2)] - loop[2:(resolution-1)]
  loop.check.right = loop[2:(resolution-1)] - loop[3:(resolution)]
  # If the signs are different, then it is a local shift
  loop.pos = c(TRUE, (sign(loop.check.left) == sign(loop.check.right)), TRUE)
  for(pos in which(loop.pos == FALSE)){ # Take the average
    loop[pos] = (loop[pos-1] + loop[pos+1])/2
  }
  E.anode$pH = loop; 
  # Loop pCO2 calculation as well, since the pCO2 function relies on the previous point
  loop = pCO2.xA.pH.A.k.beta.Na(xA = E.anode$xA[1], pH = E.anode$pH[1],
                                At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na, pCO2.prev = start.soln$p.CO2)
  for(i in 2:length(E.anode$DIC)){
    loop[i] = pCO2.xA.pH.A.k.beta.Na(xA = E.anode$xA[i], pH = E.anode$pH[i],
                                  At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na, pCO2.prev = loop[i-1])
  }
  E.anode$p.CO2 = loop
  E.anode$q = abs(E.anode$xA - E.anode$xA[1])*A.tot*z*F # Coulombs
  
  # 3 -> 4: Electrochemical reduction (xA increase to endpoint), constant DIC
  # Starting solution for initial guess: high P, low xA
  stop.soln = data.frame(p.CO2 = pCO2.out, xA = min(xA.lim))
  stop.soln$pH = pH.xA.pCO2.A.k.beta.Na(xA = stop.soln$xA, P = stop.soln$p.CO2, 
                                       At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  stop.soln$DIC = DIC.xA.pCO2.pH.A.k.beta(xA = stop.soln$xA, pCO2 = stop.soln$p.CO2, pH = stop.soln$pH, 
                                         A.tot = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2)
  # Cathode progress
  E.cathode = data.frame(DIC = stop.soln$DIC[1], xA = seq(from = stop.soln$xA[1], to = max(xA.lim), length.out = resolution))
  # Loop to solve the ieration function
  loop = pH.it.guess.DIC.At.k.beta(pH.guess = stop.soln$pH[1], xA.next = E.cathode$xA[1], DIC = E.cathode$DIC[1], 
                                       A.tot = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
  for(i in 2:length(E.cathode$DIC)){
    loop = c(loop, pH.it.guess.DIC.At.k.beta(pH.guess = loop[i-1], xA.next = E.cathode$xA[i], DIC = E.cathode$DIC[i], 
                                         A.tot = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na))
  }
  # Some iterations don't converge completely, leading to single points that deviated from the rest of the curve. This is characterized by a single point that is a local maxima or minimum. Endpoints are asusmed to be good
  loop.check.left = loop[1:(resolution-2)] - loop[2:(resolution-1)]
  loop.check.right = loop[2:(resolution-1)] - loop[3:(resolution)]
  # If the signs are different, then it is a local shift
  loop.pos = c(TRUE, (sign(loop.check.left) == sign(loop.check.right)), TRUE)
  for(pos in which(loop.pos == FALSE)){ # Take the average
    loop[pos] = (loop[pos-1] + loop[pos+1])/2
  }
  E.cathode$pH = loop;
  # Loop pCO2 calculation as well, since the pCO2 function relies on the previous point
  loop = pCO2.xA.pH.A.k.beta.Na(xA = E.cathode$xA[1], pH = E.cathode$pH[1],
                                At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na, pCO2.prev = stop.soln$p.CO2)
  for(i in 2:length(E.cathode$DIC)){
    loop[i] = pCO2.xA.pH.A.k.beta.Na(xA = E.cathode$xA[i], pH = E.cathode$pH[i],
                                  At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na, pCO2.prev = loop[i-1])
  }
  E.cathode$p.CO2 = loop
  E.cathode$q = abs(E.cathode$xA - E.cathode$xA[1])*A.tot*z*F # Coulombs
  
  # Equilibrium potential: Deviation from standard reduction potential
  E.anode$H = 10^-E.anode$pH
  E.anode$E = R*T/(z*F) * log( (1 - E.anode$xA)/E.anode$xA * 
                                   ((1 + beta1*E.anode$p.CO2 + beta2*E.anode$p.CO2^2)*k1*k2 + k1*E.anode$H + E.anode$H^2)/(k1*k2))
  E.cathode$H = 10^-E.cathode$pH
  E.cathode$E = R*T/(z*F) * log( (1 - E.cathode$xA)/E.cathode$xA * 
                                   ((1 + beta1*E.cathode$p.CO2 + beta2*E.cathode$p.CO2^2)*k1*k2 + k1*E.cathode$H + E.cathode$H^2)/(k1*k2))
  
  # Total energy
  E.cell = data.frame(q = E.anode$q, V = E.anode$E - E.cathode$E)
  # Only the positive energy demand
  E.cell = filter(E.cell, V > 0)
  len = length(E.cell$q)
  if(len == 0){
    E.cell = data.frame(q = rep(x = 0, times = 10), V = rep(x = 0, times = 10))
    len = 10
  }
  # E.anode$typ = "anode"; E.cathode$typ = "cathode"
  Energy.tot.sep = sum(0.5*(E.cell$V[2:len] + E.cell$V[1:(len-1)])*(E.cell$q[2:len] - E.cell$q[1:(len-1)]))
  
  ## Adjust the total energy by multiplying by the penalty function
  # Calculate the lean gas pressure
  # k1, k2, beta1, beta2, A.tot, Na, pCO2.in, pCO2.out
  p.lean = pCO2.lean(Na = Na, A = A.tot, beta1 = beta1, beta2 = beta2, k1 = k1, k2 = k2, pCO2.out = pCO2.out)
  penalty = weight.fun(pCO2.lean = p.lean)
  
  # Normalize by the total amount of carbon moved, i.e. units of kJ/mol
  DIC.capture = DIC.diff(Na = Na, A = A.tot, beta1 = beta1, beta2 = beta2, k1 = k1, k2 = k2, pCO2.in = pCO2.in, pCO2.out = pCO2.out)
  return(Energy.tot.sep*penalty/DIC.capture*1e-3)
}

```


```{r PCET Derived Functions: CO2 Flux}
# These equations are based on the framework for determining the CO2 flux as presented in Wilcox 2012.
Enhance.factor = function(pH, pCO2.in, A, k1, k2, beta1, beta2, pCO2){
  # Constants: general
  kw = 1e-14 # M^2
  kH = 3.4e-2; # M/atm
  z = 1 # OH- + CO2 = HCO3-
  # Constants: from Wilcox 2012
  Dco2 = 0.5e-5 # cm2/s, assume slowest due to high ionic strength
  kL = 0.1 # Assume fast mass transfer of typical range
  # Constants: average of Pocker 1997, Zeman 2007, Stolaroff 2008, Wilcox 2012
  k.rate = (6.03e3 + 6.745e3 + 8.5e3 + 12.1e3)/4
  # Constants: Lvov2012
  Doh = 5.2e-5 # cm2/s

  # Base concentration = OH + HQ- + 2Q--
  H = 10^-pH
  OH = kw/H
  base = OH + A*(2*k1*k2 + H*k1) / (H^2 + H*k1 + k1*k2*(1 + beta1*pCO2 + beta2*pCO2^2))
  
  # Interface CO2 concentration - assume 90% capture from the inlet
  CO2.int = 0.1*pCO2.in*kH
  
  # Hatta number: reaction rate / mass transfer rate
  Ha = sqrt(Dco2*base*k.rate)/kL
  # Instantaneous enhancement factor
  Ei = 1 + Doh*base / (z*Dco2*CO2.int)
  
  # return(c(Ei, Ha / tanh(Ha), Ha))
  # Check the extreme cases for E to simplify the equations
  if(Ha > 10*Ei){ # Instantaneous
    E = Ei
  } else if(Ha < Ei/2){ # Pseudo-1st order
    E = Ha / tanh(Ha)
  } else if(Ha > 3){ # 1st order
    E = Ha
  } else{ # No simplification - Solve the root that is less than Ei, as Ei is the upper bound
    x.guess = c(0.9, 0.95)*Ei
    for(i in 1:5){ # Newton's method
      y.guess = (Ha*(Ei - x.guess) / (Ei - 1)) / tanh(Ha*(Ei - x.guess) / (Ei - 1)) - x.guess
      slp.fit = (y.guess[1] - y.guess[2]) / (x.guess[1] - x.guess[2])
      E.guess = -y.guess[1]/slp.fit + x.guess[1]
      x.guess = c(0.975, 1.025)*E.guess
    }
    E = E.guess
  }
  #### Need to include order of magnitude for reaction rate with sorbent - use acid anhydride formation rate constants as estimates?
  return(E)
}

# Calculate the average kinetic driving force over the course of absorption (stage 4 -> 1)
kinetic.force = function(k1, k2, beta1, beta2, A.tot, Na, pCO2.in, pCO2.out){
  # Constants
  xA.lim = c(0.025, 0.975)
  kH = 3.4e-2; # M/atm
  # Calculate the pCO2 of the fully reduced species prior to equilibration with the gas
  out.pCO2 = pCO2.lean(Na = Na, A = A.tot, beta1 = beta1, beta2 = beta2, k1 = k1, k2 = k2, pCO2.out = pCO2.out)
  # If the minimum outlet pCO2 is greater than the target capture:
  # if(out.pCO2 > 0.1*pCO2.in | is.na(out.pCO2)){
  if(is.na(out.pCO2)){
    return(0)
  } else{
    # Calculate the pH at the start of desorption
    soln41 = data.frame(xA = max(xA.lim), p.CO2 = out.pCO2)
    # Solve pH with multiple cores
    soln41$pH = pH.xA.pCO2.A.k.beta.Na(xA = soln41$xA, P = soln41$p.CO2, 
                         At = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, Na = Na)
    soln41$E = Enhance.factor(pH = soln41$pH, pCO2.in = pCO2.in, A = A.tot, k1 = k1, k2 = k2, beta1 = beta1, beta2 = beta2, pCO2 = soln41$p.CO2)

    # Calculate the concentration difference between the interface and the bulk. Assuming 90% capture
    soln41$delC = (0.1*pCO2.in - out.pCO2)*kH
    # Flux: delC * kL * E, assume kL = 0.1 cm/s as in the enhancement factor calculation
    # Unit conversion: L to cm3, cm2 to m2
    flux = soln41$delC*soln41$E*0.1 * (1/1e3) * (100^2)
    # return(soln41)
    return(signif(flux, 5)) # Highest driving force at outlet
    # return(soln41)
  }
}

```


To work with GPareto, the two objective functions need to combined, and the input should be a matrix, not a dataframe. I account for this with a wrapper function to simplify the process.

```{r}
PCET.obj.flu = function(inputs){
  # Inputs is a matrix where each row is an instance and each column is a specific variable:
  # From left to right, the columns are:
  # pka1, err.pka2, log10(A.tot), Na/A.tot
  # For the functions, the variables should be:
  # k1, k2, A.tot, Na
  # The use of log units and ratios helps alleviate resolution issues associated with spanning multiple orders of magnitude
  # The use of the error of pKa2 removes the correlation between the two variables
  
  # Storing the proper information.
  if(is.matrix(inputs)){
    dat = data.frame(k1 = 10^-inputs[,1],
                     k2 = 10^-(inputs[,1] + inputs[,2]),
                     A.tot = 10^inputs[,3],
                     Na = 10^inputs[,4]*10^inputs[,3])
  } else{
    # The optimization function sometimes stores as a vector instead of as a matrix if it is just a single point
    dat = data.frame(k1 = 10^-inputs[1],
                     k2 = 10^-(inputs[1] + inputs[2]),
                     A.tot = 10^inputs[3],
                     Na = 10^inputs[4]*10^inputs[3])
  }
  # The following conditions are assumed for PCET from flue gas
  beta1 = 0; beta2 = 0;
  pCO2.in = 0.15; pCO2.out = 1;
  
  # The functions require substantial computation, so each row has to be processed independently
  energy = c(); flux = c()
  for(i in 1:nrow(dat)){
    energy[i] = Energy.tot(k1 = dat$k1[i], k2 = dat$k2[i], 
                           beta1 = 0, beta2 = 0, 
                           A.tot = dat$A.tot[i], Na = dat$Na[i], 
                           pCO2.in = 0.15, pCO2.out = 1)
    flux[i] = kinetic.force(k1 = dat$k1[i], k2 = dat$k2[i], 
                            beta1 = 0, beta2 = 0, 
                            A.tot = dat$A.tot[i], Na = dat$Na[i], 
                            pCO2.in = 0.15, pCO2.out = 1)
  }
  # Obtain the negative of the flux so it is a minimization function for the optimization search
  return(c(energy, -flux)) 
}

```

# Target values

For both the energy and flux, the most logical comparison is to the industry standard of 30wt% MEA.

The energy demand for this process is 90 - 130 kJ/mol C.
Lin, Y. J.; Chen, E.; Rochelle, G. T. Pilot plant test of the advanced ash stripper for CO2 capture. Faraday Discussions 2016, 192, 3758.
Using the median value of this range (110 kJ/mol) and a thermal-to-electricity conversion of 30% (typical for coal power plants), the energy target is 33 kJe/mol C of electrical energy.

For the flux, using the Film Model as described in Wilcox 2012
Wilcox, J. Carbon Capture; Springer New York, 2012. https://doi.org/10.1007/978-1-4614-2215-0.

using the following constants (same source or listed above in the function):
* 30wt% is approximately 5 M
* Diffusion coefficient of MEA ~ diffusion coefficient of CO2 (as above: 0.5e-5 cm^2/s)
* Henry's law constant: 0.034 mol/L*atm
* 90% of the CO2 was captured from a 15% inlet
* reaction rate constant = 7570 L/mol*s
* reactor mass transfer coefficient (as above) = 0.1 cm/s (assume a fast design)

hatta number = sqrt( D k C) / kL
E = 1 + D*cMEA / (stoichio * Dco2 * Cco2)

```{r}
C.MEA = 5
D.CO2 = 0.5e-5
D.MEA = D.CO2
C.CO2 = 0.034*(1 - 0.90)*0.15
k = 7570
kL = 0.1
# Calculate the Hatta number
Ha = sqrt(D.MEA * k * C.MEA)/kL
# Limiting enhancement factor
Ei = 1 + D.MEA*C.MEA / (1 + D.CO2 * C.CO2)

Ha
Ei
# From these values, this is the fast pseudo-first order reaction regime, so the flux can be estimated as
flux = sqrt(D.CO2 * k * C.MEA) * C.CO2 * (1/1e3) * (100^2) # Since concentration was in mol/L, converting to mol/m^2*s
flux*1e3 # in mmol/m^2*s for comparison

```

Rounding, the flux is 2.2 mmol/m^2*s.
While this would be the ideal cutoff, to obtain a good range of values, anything above 1/10th of this flux should be viable.

